\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=0.6in]{geometry}
\usepackage{fontspec}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{4pt}{%
    \large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-6pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{1pt}
\setlength{\topsep}{2pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\LARGE\bfseries Ronak Punase}\par\vspace{2pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http:/ronak.punase.dev}{ronak.punase.dev}
    }
  \end{center}
  \vspace{-10pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty}

\begin{document}
\small

\maketitle
\vspace{6pt}

% ---------- SUMMARY ----------
\section{Summary}
Data-driven Flutter Engineer with strong native Android/iOS experience and expertise in statistical analysis and modeling. Proven experience in developing data-driven strategies in collaboration with cross-functional teams. Expert at communicating findings and insights clearly.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Data Analyst} \hfill March 2024 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Facilitated data-driven decision making by developing and implementing advanced statistical models and algorithms.
  \item Contributed to the enhancement of the product line by applying problem-solving skills and data analysis.
  \item Presented data-driven insights to the management and contributed to setting the company's strategic direction.
  \item Worked in close collaboration with cross-functional teams to align the company's data initiatives with business objectives.
  \item Mastered the art of learning from data and used this insight to improve business performance and processes.
  \item Led the transition to a more data-driven culture, strengthening the company's competitive advantage.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}

\org{Data Analysis Toolkits} \bull Own project \hfill \place{Remote}
\begin{itemize}
  \item Analyzed complex datasets using advanced statistical techniques to extract actionable insights.
  \item Built and validated predictive models and machine learning algorithms.
  \item Developed and maintained robust data pipelines, ensuring data integrity and usability.
  \item Created data visualizations and interactive dashboards to present data-driven insights in a meaningful way.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Data Analytics:} Statistical modeling, machine learning, predictive modeling, data mining, optimization \\
\textbf{Programming:} Python (NumPy, Pandas, Matplotlib, Seaborn), R, SQL, Java, Flutter, Android (Kotlin), iOS (Swift) \\
\textbf{Data Visualization:} Tableau, PowerBI, ggplot \\
\textbf{Databases:} MySQL, PostgreSQL, MongoDB, Firestore

% ---------- EDUCATION ----------
\section{Education}
\textbf{Master of Science in Data Science} \\
\org{RGPV University} \bull \place{Bhopal, MP} \bull 2024 \\
Relevant coursework: Statistical modeling, Machine learning, Advanced Analytics, Big data 

\textbf{Bachelors of Engineering in Computer Science} \\
\org{RGPV University} \bull \place{Bhopal, MP} \bull 2021 \bull GPA: 4.25/5.0 

\end{document}