\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Extensive project management experience with responsibilities across defining scope, building and executing Agile plans, schedules, and budgets, and effectively tracking project performance. Experienced with ML, Node.js, React Native, Flutter, and Angular. Proactively anticipate risks and issues and effectively manage benefits. Strong communication skills proficient in building and managing teams and closely interact with clients and internal teams. Notably detail-oriented and commercial-minded with a good history of delivering projects on schedule, within budget, exceeding expectations.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Agile Project Manager} \hfill October 2027 -- Present \\
\org{Clarity Tech} \hfill \place{Mumbai, India}
\begin{itemize}
  \item Defined end-to-end delivery scope of web, mobile, and other digital projects.
  \item Built and executed Agile plans, schedules, and budgets.
  \item Organized complex cross-functional activities and proactively managed benefits and risks.
  \item Monitored performance, tracked progress with PM tools, and provided weekly status updates.
  \item Successfully led operational, financial, technical workstreams and closely coordinated with clients and internal teams.
\end{itemize}


\role{SDE-Tech Lead} \hfill March 2025 -- September 2027 \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Managed backend services with Node.js and also embedded ML models in these services.
  \item Built and managed cross-platform mobile applications using Flutter and React Native.
  \item Designed frontend services with Angular.
  \item Incrementally implemented Agile methodologies and enforced Agile practices for project delivery.
  \item Conducted weekly status meetings and effectively communicated project progress to all stakeholders.
\end{itemize}

% ----------Education ----------
\section{Education}
\textbf{Masters of Business Administration} \bull Cleary University \bull Michigan, USA \bull 2013 \bull GPA: 3.8/4.0 \\
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2011 \bull GPA: 4.25/5.0

% ---------- PROJECTS ----------
\section{Projects}

\begin{itemize}
  \item Managed the end-to-end delivery of ‘MyMoney’ a financial tracking app ensuring it is delivered within a stipulated timeline.
  \item Acted as the project lead for ‘Majestic UI’, taking responsibility for project governance, planning, stakeholder management, and successful delivery.
  \item Led a team of developers for the ‘The CS Guy’ to ensure code quality, adherence to standards, and to provide mentorship.
\end{itemize}
% ---------- SKILLS ----------
\section{Skills}
\textbf{Programming:} Python, C++, Java \\
\textbf{Web:} HTML5, CSS, JavaScript, TypeScript, Node.js, Angular \\
\textbf{Mobile:} React Native, Flutter, Dart, Android (Java, Kotlin), iOS (Swift) \\
\textbf{Machine Learning:} Scikit-learn, TensorFlow, Pytorch \\
\textbf{Project Management:} Agile Methodologies, Scrum, Kanban \\
\textbf{Databases:} MySQL, MongoDB, PostgreSQL \\
\textbf{Version Control:} Git, GitHub \\
\textbf{Cloud:} AWS, GCP, Azure 

\end{document}