\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} 

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Highly skilled Flutter developer with experience in building, testing, optimizing, and maintaining Android/iOS apps. Proficient in Flutter/Dart, Firebase's suite of functionalities, state management (Provider, Bloc, GetX), and REST API integration with adeptness in MVC/MVVM concepts. Demonstrated strong problem-solving abilities, commitment to clean, scalable code and versed with Git/version control. Experienced in managing Play Store/App Store releases.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Developed Android/iOS apps with Flutter/Dart, integrated Firebase's suite including Authentication, Firestore, and push notifications.
  \item Implemented REST APIs and JSON integration, providing seamless functionality and data transfer.
  \item Integrated Firebase-based state management using Provider, Bloc, and GetX frameworks.
  \item Collaborated with UI/UX and backend teams to deliver scalable, high-performing apps.
  \item Employed Git/version controls for efficient code management, ensuring adherence to clean coding norms.
  \item Managed Play Store/App Store releases, maintaining exceptional app performance and user experience.
\end{itemize}
\vspace{12pt}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Drew upon strong knowledge in Flutter/Dart to develop highly functional Android/iOS apps.
  \item Implemented REST APIs and JSON integrations for flawless data transfer.
  \item Integrated Firebase (Authentication, Firestore, push notification) for secure and efficient app features.
  \item Utilized state management frameworks such as Provider, Bloc, and GetX for effective state management.
  \item Used well-developed debugging skills to maintain high app performance.
  \item Demonstrated proficiency in Git and version control for efficient code management.
  \item Managed app releases on Play Store/App Store, ensuring high app quality and performance.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Built the app using Flutter/Dart, integrating REST APIs and JSON for efficient data processing.
  \item Used Firebase (Authentication, Firestore, push notifications) to add secure and efficient features.
  \item Incorporated state management (Provider, Bloc, GetX) for effective handling of app state.
  \item Used strong debugging skills to improve app performance.
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Developed the app with Flutter/Dart, with integration of REST APIs and JSON for seamless data transfer.
  \item Incorporated extensive use of Firebase (Authentication, Firestore, push notifications) for feature integration.
  \item Implemented state management (Provider, Bloc, GetX) for effective handling of app state.
  \item Devised debugging strategies to ensure high app performance.
\end{itemize}

\org{The CS Guy} \bull Passion Project \bull \href{https://youtube.com/@TheCSGuy}{youtube.com/@TheCSGuy}
\begin{itemize}
  \item Used advanced state management (Bloc, Riverpod, Provider) practices to build efficient Android/iOS apps with Flutter/Dart.
  \item Incorporated Firebase (Authentication, Firestore, push notifications) for secure and smooth app performance.
  \item Debugged and made improvements to maintain high app performance.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Flutter:} Dart, state management (Provider/Bloc/GetX), MVVM architecture, testing and debugging, REST API and JSON integration, Firebase (Authentication, Firestore, push notifications) \\
\textbf{Mobile:} Android (Java, Kotlin), iOS (Swift), Play Store/App Store releases \\
\textbf{Web:} REST integration \\
\textbf{Backend:} Firebase \\
\textbf{Source Control:} Git, version control \\
\textbf{Miscellaneous:} Strong problem-solving, code scalability, collaboration

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors in Information Technology} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}