
\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - CANDIDATE\_NAME},
  pdfauthor={CANDIDATE\_NAME},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}
\newcommand{\placeholder}[1]{\lbrack #1\rbrack}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries \placeholder{CANDIDATE\_NAME}}\par\vspace{6pt}
    {\color{Primary}
      \placeholder{LOCATION} \bull
      \blackLink{mailto:\placeholder{EMAIL}}{\placeholder{EMAIL}} \bull
      \placeholder{PHONE} \bull
      \blackLink{\placeholder{LINKEDIN\_URL}}{\placeholder{LINKEDIN\_HANDLE}} \bull
      \blackLink{\placeholder{WEBSITE\_URL}}{\placeholder{WEBSITE\_DOMAIN}}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Experienced backend engineer with over 3 years in designing and implementing transactional systems, particularly in the fintech sector. Proven track record in leading integration projects, ensuring system correctness, and enhancing payment processing capabilities.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Lead Backend Engineer} \hfill \placeholder{START\_DATE} -- \placeholder{END\_DATE} \\
\org{\placeholder{COMPANY\_NAME}} \bull \href{\placeholder{COMPANY\_URL}}{\placeholder{COMPANY\_DOMAIN}} \hfill \place{\placeholder{LOCATION}}
\begin{itemize}
  \item Designed and enforced a canonical payment state machine, improving transaction reliability and efficiency.
  \item Built and maintained PaymentIntent and ledger models, ensuring accurate financial reporting and reconciliation.
  \item Led integration with multiple payment gateways, including Stripe and Braintree, enhancing payment processing capabilities.
  \item Defined idempotency guarantees across APIs and jobs, reducing transaction errors and improving user experience.
  \item Owned retry and failover logic, ensuring system resilience and operational excellence.
\end{itemize}
\vspace{12pt}

% Add more experience entries above this line, each separated by \vspace{12pt}

% ---------- PROJECTS ----------
\section{Projects}
\org{Payment Processing System} \bull \textit{Fintech Project} \bull \href{\placeholder{PROJECT\_URL}}{\placeholder{PROJECT\_DOMAIN}}
\begin{itemize}
  \item Developed a robust payment processing system that handles retries, duplicate events, and partial failures.
  \item Implemented webhook ingestion pipelines with replay safety, ensuring data integrity and system reliability.
\end{itemize}

% Add more projects above this line, each separated by a blank line

% ---------- SKILLS ----------
\section{Skills}
\textbf{Programming Languages:} Python, Java, SQL \\
\textbf{Frameworks:} Django, Flask \\
\textbf{Tools:} Git, Docker, Kubernetes \\
\textbf{Payment Systems:} Stripe, Braintree, Adyen, Checkout \\
\textbf{Concepts:} State Machines, Idempotency, Distributed Systems, Relational Databases, Ledger Models \\

% ---------- EDUCATION ----------
\section{Education}
\textbf{\placeholder{DEGREE\_NAME}} \bull \placeholder{INSTITUTION\_NAME} \bull \placeholder{LOCATION} \bull \placeholder{GRADUATION\_YEAR} \bull GPA: \placeholder{GPA}/\placeholder{SCALE}

\end{document}
