\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Competitive when learning, collaborative when building. I am skilled in full-stack web application development, with proficiency in C\#.NET, ASP.NET, HTML5, CSS3, JavaScript, and SQL Server. I have extensive experience in designing, implementing, testing, and documenting new features and enhancements for flagship products. I am adept at working in global teams and providing production support. I also have a strong background in teaching and building countless professional, personal, and freelance projects in Flutter.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Software Developer} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Designed and developed new features and enhancements for flagship products, ensuring high-quality deliverables.
  \item Implemented unit tests and maintained comprehensive documentation for developed features.
  \item Worked effectively with global teams, coordinating with members from various countries.
  \item Addressed and resolved production support tickets promptly.
\end{itemize}
\vspace{12pt}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Integrated \textbf{Agora’s} native Android and iOS SDK into a Flutter plugin, enabling seamless whiteboard and networking capabilities while reducing development time by 25\%.
  \item Established a reliable video calling mechanism by integrating FCM, \textbf{iOS CallKit}, and Flutter, delivering functionality on par with WhatsApp.
  \item Developed a \textbf{Flutter video calling plugin} inspired by getstream.io with an abstract ringer for easy Android/iOS integration using native CallKit, cutting development time by over 75\%.
  \item Implemented responsive designs for tablet and iPad, ensuring pixel-perfect UI across diverse screen sizes.
  \item Built a dedicated Flutter app from scratch for tutors, enabling collaboration between 50,000+ students and tutors.
  \item Shipped an \textbf{Instagram Stories–inspired} feature using advanced video caching and Flutter best practices to reduce load times by 35\%.
  \item Built admin tools including a Content Management System and Customer Care Platform on Flutter Web.
  \item Led revisions and seamless deployment of \textbf{PuStack} and \textbf{PuStack Tutor} apps on \textbf{Play Store} and \textbf{App Store}.
  \item Designed a resilient call billing and payout system for instructors, increasing engagement by 25\%.
\end{itemize}


% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Expense tracking app, built in Flutter, published to play store and app store.
  \item Parses users bank statement locally and stores the transactions in local DB.
  \item Advanced dart usage: extensions, factory constructors, MVVM with Bloc for state management.
  \item Fetches last 10 SMS to extract any transaction details and store them in local DB.
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Designed a Flutter UI system with reusable components and a CLI delivery system.
  \item Created a Next.js platform hosting Flutter WebViews to encourage open-source contributions.
  \item Reached 12,000+ YouTube views within one week of release.
\end{itemize}

\org{The CS Guy} \bull Passion Project \bull \href{https://youtube.com/@TheCSGuy}{youtube.com/@TheCSGuy}
\begin{itemize}
  \item Produced tutorials emphasizing Flutter’s UI capabilities, garnering 200,000+ views.
  \item Delivered a free Flutter course reaching 150,000+ viewers.
  \item Demonstrated advanced state management (Bloc, Riverpod, Provider) and TDD practices.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Technical Skills:}
\begin{itemize}
  \item Proficiency in C\#.NET and ASP.NET with at least 3 years of experience.
  \item Experience with the .NET ecosystem, including .NET Framework, .NET Core, and .NET 5.
  \item Strong knowledge of RESTful API frameworks.
  \item Frontend development skills in HTML5, CSS3, and JavaScript.
  \item Experience with unit testing frameworks like XUnit.net or NUnit.
  \item Proficiency in RDBMS, particularly SQL Server or other relational databases.
  \item Familiarity with code repositories such as Git or Azure Repos.
  \item Exposure to DevOps practices, including CI/CD and containerization.
\end{itemize}

\textbf{Additional Skills:}
\begin{itemize}
  \item Ability to develop solutions independently, ensuring high-quality and issue-free deliverables.
  \item Provide guidance and conduct code reviews for junior developers.
  \item Create and maintain technical design documents.
  \item Strong verbal and written communication skills, with experience in environments where clients are offshore.
  \item Experience working in agile environments, such as Scrum or Kanban.
  \item Proficiency in using collaboration and project management tools like MS Teams and JIRA.
\end{itemize}

% ---------- EDUCATION ----------
\section{Education}
\textbf{B.Tech/B.E. in Computer Science} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}