\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Competitive when learning, collaborative when building. I am skilled in C\#.NET and ASP.NET with proficiency in the .NET ecosystem, including .NET Framework, .NET Core, and .NET 5. I have experience with RESTful API frameworks and frontend development skills in HTML5, CSS3, and JavaScript. I have worked with unit test frameworks like XUnit.net or NUnit and have proficiency in RDBMS, preferably SQL Server or other relational databases. I have experience with code repositories such as Git or Azure Repos and exposure to DevOps practices, including CI/CD and containerization. I have the ability to work independently on both frontend and backend development and write code adhering to standard-driven technical approaches to produce quality deliverables. I have experience in mentoring and conducting code reviews for junior developers and creating technical design documents. I have strong interpersonal skills and experience working in offshore client environments. I have experience working in agile environments, such as Scrum or Kanban, and am comfortable using collaboration and project tools like MS Teams and JIRA.


% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Designed and implemented new features and enhancements for flagship products.
  \item Performed unit testing and documentation of developed features.
  \item Deployed new features and enhancements following SDLC best practices.
  \item Addressed production support tickets.
  \item Collaborated with global teams across various locations.
\end{itemize}
\vspace{12pt}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Integrated \textbf{Agora’s} native Android and iOS SDK into a Flutter plugin, enabling seamless whiteboard and networking capabilities while reducing development time by 25\%.
  \item Established a reliable video calling mechanism by integrating FCM, \textbf{iOS CallKit}, and Flutter, delivering functionality on par with WhatsApp.
  \item Developed a \textbf{Flutter video calling plugin} inspired by getstream.io with an abstract ringer for easy Android/iOS integration using native CallKit, cutting development time by over 75\%.
  \item Implemented responsive designs for tablet and iPad, ensuring pixel-perfect UI across diverse screen sizes.
  \item Built a dedicated Flutter app from scratch for tutors, enabling collaboration between 50,000+ students and tutors.
  \item Shipped an \textbf{Instagram Stories–inspired} feature using advanced video caching and Flutter best practices to reduce load times by 35\%.
  \item Built admin tools including a Content Management System and Customer Care Platform on Flutter Web.
  \item Led revisions and seamless deployment of \textbf{PuStack} and \textbf{PuStack Tutor} apps on \textbf{Play Store} and \textbf{App Store}.
  \item Designed a resilient call billing and payout system for instructors, increasing engagement by 25\%.
\end{itemize}


% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Expense tracking app, built in Flutter, published to play store and app store.
  \item Parses users bank statement locally and stores the transactions in local DB.
  \item Advanced dart usage: extensions, factory constructors, MVVM with Bloc for state management.
  \item Fetches last 10 SMS to extract any transaction details and store them in local DB.
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Designed a Flutter UI system with reusable components and a CLI delivery system.
  \item Created a Next.js platform hosting Flutter WebViews to encourage open-source contributions.
  \item Reached 12,000+ YouTube views within one week of release.
\end{itemize}

\org{The CS Guy} \bull Passion Project \bull \href{https://youtube.com/@TheCSGuy}{youtube.com/@TheCSGuy}
\begin{itemize}
  \item Produced tutorials emphasizing Flutter’s UI capabilities, garnering 200,000+ views.
  \item Delivered a free Flutter course reaching 150,000+ viewers.
  \item Demonstrated advanced state management (Bloc, Riverpod, Provider) and TDD practices.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{.NET:} C\#.NET, ASP.NET, .NET Framework, .NET Core, .NET 5 \\
\textbf{Frontend:} HTML5, CSS3, JavaScript \\
\textbf{Testing:} XUnit.net, NUnit \\
\textbf{Database:} SQL Server, RDBMS \\
\textbf{Version Control:} Git, Azure Repos \\
\textbf{DevOps:} CI/CD, Containerization \\
\textbf{Collaboration Tools:} MS Teams, JIRA \\
\textbf{Agile:} Scrum, Kanban \\
\textbf{Flutter:} Bloc, Navigator 2.0, Provider, Riverpod, Freezed, GetIt, GoRouter, MVVM, Unit Testing \\
\textbf{Mobile:} Android (Java, Kotlin, Jetpack Compose), iOS (Swift) \\
\textbf{Web:} ReactJS, NextJS (TypeScript), ExpressJS, Zustand, Redux \\
\textbf{Backend:} Firebase, MongoDB, Prisma, Supabase, ConvexDB \\
\textbf{Source Control:} Git, GitHub, GitHub Actions (CI/CD)

% ---------- EDUCATION ----------
\section{Education}
\textbf{B.Tech in Computer Science} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}