Here is your updated resume with an emphasis on Flutter development. I have tweaked the "Summary" section and reordered the "Skills" section to specifically highlight your Flutter-related skills first. Your Flutter experience is now also more prominent in the "Experience" section.

\begin{document}

\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Collaborative and experienced Flutter developer with over 4 years of hands-on experience building production Flutter apps with Dart, proficient in state management (Bloc/Provider/Riverpod), navigation, and async programming. Skilled in REST/GraphQL API integration, Firebase and analytics, push notifications, and implementing clean architecture with a focus on SOLID principles, performance and accessibility. Proven record of collaboration in Agile/Scrum environments with strong documentation skills, intricate Git habits, and excellent English communication aptitude.


% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE - Flutter} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Led the development and stabilization of a unified CI/CD pipeline for Android, iOS, Firebase Distribution, and Shorebird, reducing distribution time by several hours and development time by 25\%.
  \item Developed Flutter UI components using reliable state management tools, such as Riverpod.
  \item Implemented REST/GraphQL API integration for service-to-service communication.
  \item Architected a design system governed by Figma tokens to build resilient Dart-based UIs.
\end{itemize}

\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Leveraged unit/widget/integration testing, code reviews, and CI/CD practices to improve overall project code quality.
  \item Managed extensive app store releases and led revisions of PuStack and PuStack Tutor apps in both, Play Store and App Store.
  \item Developed a resilient call billing and payout system for instructors, increasing engagement by 25\%.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}
\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Developed an expense tracking app using advanced dart usage such as extensions, factory constructors, and Bloc for state management.
  \item Handled REST/GraphQL API interactions, organized unit/widget/integration testing, and ensured high-performance, robust code via CI/CD pipeline.
\end{itemize}


% ---------- SKILLS ----------
\section{Skills}

\textbf{Flutter:} Dart, Bloc, Provider, Riverpod, Freezed, GetIt, GoRouter, MVVM, Unit Testing \\
\textbf{Mobile:} Android (Java, Kotlin, Jetpack Compose), iOS (Swift) \\
\textbf{Web:} ReactJS, NextJS (TypeScript), ExpressJS, Zustand, Redux \\
\textbf{Backend:} Firebase, MongoDB, Prisma, Supabase, ConvexDB \\
\textbf{Source Control:} Git, GitHub, GitHub Actions (CI/CD)

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}