\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Competitive when learning, collaborative when building. I am skilled in native Android/iOS apps along with that I have extensive experience in teaching and building countless professional, personal and freelance projects in Flutter. I have a strong command over the Flutter/Dart ecosystem, including Bloc/Cubit, Freezed with build\_runner, JSON serialization, REST API integration, and dependency injection using getIt/injectable. I am also familiar with Riverpod and Clean Architecture. I am comfortable working both collaboratively and independently, and I am always eager to learn and share knowledge. I am fluent in English and Polish at a B2 level and have experience with Jira and agile workflows (Kanban/Scrum).

% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Implemented a responsive and resilient design system governed by \textbf{Figma tokens}.
  \item Built a new, dynamic UI using advanced Dart features (mixins, factory constructors, detailed enums), improving overall project code quality.
  \item Developed and stabilized multiple CI/CD workflows, reducing build failures by 40\%.
  \item Implemented a unified CI/CD pipeline for Android, iOS, Firebase Distribution, and Shorebird, reducing distribution time by several hours (60-70\%).
  \item Replaced GitHub-hosted runners with local runners, reducing infrastructure costs by 150\% and speeding up builds by 25\%.
  \item Re-implemented the cart as a local-first system, improving add-to-cart speed and delivering a noticeably smoother UX.
\end{itemize}
\vspace{12pt}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Integrated \textbf{Agora’s} native Android and iOS SDK into a Flutter plugin, enabling seamless whiteboard and networking capabilities while reducing development time by 25\%.
  \item Established a reliable video calling mechanism by integrating FCM, \textbf{iOS CallKit}, and Flutter, delivering functionality on par with WhatsApp.
  \item Developed a \textbf{Flutter video calling plugin} inspired by getstream.io with an abstract ringer for easy Android/iOS integration using native CallKit, cutting development time by over 75\%.
  \item Implemented responsive designs for tablet and iPad, ensuring pixel-perfect UI across diverse screen sizes.
  \item Built a dedicated Flutter app from scratch for tutors, enabling collaboration between 50,000+ students and tutors.
  \item Shipped an \textbf{Instagram Stories–inspired} feature using advanced video caching and Flutter best practices to reduce load times by 35\%.
  \item Built admin tools including a Content Management System and Customer Care Platform on Flutter Web.
  \item Led revisions and seamless deployment of \textbf{PuStack} and \textbf{PuStack Tutor} apps on \textbf{Play Store} and \textbf{App Store}.
  \item Designed a resilient call billing and payout system for instructors, increasing engagement by 25\%.
\end{itemize}


% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Expense tracking app, built in Flutter, published to play store and app store.
  \item Parses users bank statement locally and stores the transactions in local DB.
  \item Advanced dart usage: extensions, factory constructors, MVVM with Bloc for state management.
  \item Fetches last 10 SMS to extract any transaction details and store them in local DB.
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Designed a Flutter UI system with reusable components and a CLI delivery system.
  \item Created a Next.js platform hosting Flutter WebViews to encourage open-source contributions.
  \item Reached 12,000+ YouTube views within one week of release.
\end{itemize}

\org{The CS Guy} \bull Passion Project \bull \href{https://youtube.com/@TheCSGuy}{youtube.com/@TheCSGuy}
\begin{itemize}
  \item Produced tutorials emphasizing Flutter’s UI capabilities, garnering 200,000+ views.
  \item Delivered a free Flutter course reaching 150,000+ viewers.
  \item Demonstrated advanced state management (Bloc, Riverpod, Provider) and TDD practices.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Flutter:} Bloc, Cubit, Freezed with build\_runner, JSON serialization, REST API integration, getIt/injectable, Riverpod, Clean Architecture \\
\textbf{Mobile:} Android (Java, Kotlin, Jetpack Compose), iOS (Swift) \\
\textbf{Web:} ReactJS, NextJS (TypeScript), ExpressJS, Zustand, Redux \\
\textbf{Backend:} Firebase, MongoDB, Prisma, Supabase, ConvexDB \\
\textbf{Source Control:} Git, GitHub, GitHub Actions (CI/CD) \\
\textbf{Project Management:} Jira, Agile workflows (Kanban/Scrum)

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}