\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center>
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Skilled digital project manager with extensive knowledge in native Android/iOS apps and Flutter. Proven track record in defining project scopes, implementation of detailed timelines, management of budgets, and delivery of projects within scope.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Digital Project Manager / SDE} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Acted as the lead in defining project scope and plans along with executing detailed timelines.
  \item Managed project budgets and oversaw the business plan execution.
  \item Coordinated cross-functional teams to drive online initiatives and mobile app development.
  \item Developed and stabilized multiple CI/CD workflows, reducing build failures by 40\%.
  \item Implemented a unified CI/CD pipeline for Android, iOS, Firebase Distribution, and Shorebird, reducing distribution time by several hours (60-70\%).
  \item Actively involved in risk management, leading to the development of robust mitigation plans.
  \item Regularly communicated with clients to ensure product delivery is aligned with client expectations.
  \item Re-implemented the cart as a local-first system, improving add-to-cart speed and delivering a noticeably smoother UX.
\end{itemize}
\vspace{12pt}
\role{Flutter Developer / Project Manager} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Oversaw the project management, including defining workstream protocols and coordinating with clients and cross-functional teams.
  \item Integral in driving online initiatives and mobile app development.
  \item Developed a \textbf{Flutter video calling plugin} inspired by getstream.io with an abstract ringer for easy Android/iOS integration using native CallKit, cutting development time by over 75\%.
  \item Managed a complex meeting schedule to ensure collaboration and productivity across all teams.
  \item Led revisions and seamless deployment of \textbf{PuStack} and \textbf{PuStack Tutor} apps on \textbf{Play Store} and \textbf{App Store}.
  \item Acted as the main point of contact for clients, maintaining regular communication to ensure the project is in line with client expectations.
  \item Implemented responsive designs for tablet and iPad, ensuring pixel-perfect UI across diverse screen sizes.
  \item Built a dedicated Flutter app from scratch for tutors, enabling collaboration between 50,000+ students and tutors.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Project Management:} Scope & Plan Definition, Timeline Execution, Budget Management, Risk Mitigation \\
\textbf{Flutter:} Bloc, Navigator 2.0, Provider, Riverpod, Freezed, GetIt, GoRouter, MVVM, Unit Testing \\
\textbf{Mobile:} Android (Java, Kotlin, Jetpack Compose), iOS (Swift) \\
\textbf{Web:} ReactJS, NextJS (TypeScript), ExpressJS, Zustand, Redux \\
\textbf{Backend:} Firebase, MongoDB, Prisma, Supabase, ConvexDB \\
\textbf{Source Control:} Git, GitHub, GitHub Actions (CI/CD)

% ---------- EDUCATION ----------
\section{Education}
\textbf{Masters in Project Management} \bull XYZ University \bull Bhopal, MP \bull 2023 \bull GPA: 4.5/5.0 \\
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}