\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase for Flutter Developer Role},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Custom commands ----------
\newcommand{\resItem}[2]{\item \textbf{#1:} #2}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Results-oriented Flutter developer seeking the opportunity to utilise extensive experience in mobile application development, UI design, state management, CI/CD pipeline implementation, application security, bug fixing, and code optimization. Well-versed in writing unit/widget/integration tests, conducting code reviews and integrating backend APIs/SDKs. Proven ability in improving app performance and reliability, ensuring accessibility, analytics, security, and privacy compliance.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Developed responsive, polished UIs focused on performance and reliability, in line with product/design requirements.
  \item Engaged in writing unit/widget/integration tests and participated in code reviews; optimized code and debugged complex issues for rapid feature delivery while maintaining code quality.
  \item Built and maintained cross-platform mobile apps using Dart, ensuring smooth functioning and seamless User Experience (UX).
  \item Collaborated closely with product, design, and backend teams to align development efforts with strategic goals.
  \item Ensured accessibility, analytics, security, and privacy compliance in app development.
  \item Contributed to robust CI/CD pipelines and monitoring implementation, reducing build time and errors.
\end{itemize}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Designed and built cross-platform mobile apps using the Flutter framework and Dart programming language, ensuring applications ran seamlessly on all platforms.
  \item Improved app functionality and user experience by integrating with backend APIs/SDKs.
  \item Developed and implemented robust state management and clean architecture, enabling efficient scaling of the application.
  \item Participated in agile meetings and produced high-quality software within the scheduled timeline.
  \item Assured smooth transition and debugging of applications, guaranteeing rapid deployment and high-quality code.
  \item Spearheaded the set-up and maintenance of CI/CD pipelines, facilitating quick and automatic code deployments.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}
\begin{itemize}
  \resItem{Development}{Dart, Flutter, Android (Java, Kotlin), iOS (Swift), Backend: (Firebase, MongoDB)}
  \resItem{UI Design}{Responsive UIs, UX, Figma, Material Design, Apple UI guidelines}
  \resItem{State Management}{Bloc, Provider, Riverpod, GetIt, GoRouter, MVVM}
  \resItem{Testing}{Unit, Widget, Integration testing, automated tests}
  \resItem{Version Control \& CI/CD Implementation}{Git, GitHub, GitHub Actions}
  \resItem{Collaborative Development}{Code Reviews, Team Collaboration}
  \resItem{Compliance}{Accessibility standards, Security requirements, Privacy regulations}
\end{itemize}

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}