\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Driven Software Engineer with a strong background in Flutter, Mobile Development and iOS runtime. Proficient in implementing native integrations in iOS for effective responsiveness. 2+ years experience in iOS app development with Swift and Objective-C. Passionate about optimizing applications for high performance, low latency, and maximum efficiency.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Software Development Engineer} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Enhanced app performance by optimizing startup time, memory usage, and frame rates to achieve parity with native apps.
  \item Tracked and analyzed Apple platform changes and WWDC updates to deliver day-zero compatibility with new iOS versions.
  \item Implemented a responsive and resilient design system governed by \textbf{Figma tokens}.
  \item Built a new, dynamic UI using advanced Dart features (mixins, factory constructors, detailed enums), improving overall project code quality.
  \item Developed and stabilized multiple CI/CD workflows, reducing build failures by 40\%.
  \item Implemented a unified CI/CD pipeline for Android, iOS, Firebase Distribution, and Shorebird, reducing distribution time by several hours (60-70\%).
  \item Replaced GitHub-hosted runners with local runners, reducing infrastructure costs by 150\% and speeding up builds by 25\%.
\end{itemize}
\vspace{12pt}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Built and optimized Flutter’s iOS runtime by integrating complex native integrations for high fidelity and responsiveness.
  \item Developed a \textbf{Flutter video calling plugin} inspired by getstream.io with an abstract ringer for easy Android/iOS integration using native CallKit, cutting development time and achieving high fidelity and responsiveness.
  \item Integrated \textbf{iOS CallKit} into the application, achieving functionality on par with native iOS apps.
  \item Led revisions and seamless deployment of \textbf{PuStack} and \textbf{PuStack Tutor} apps on \textbf{App Store}, ensured compatibility with new iOS/Swift versions.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Skills:} iOS App Development, Swift, Objective-C, Memory Profiling, Flutter, Android App Development \\
\textbf{Tools:} Firebase, MongoDB, Git, GitHub Actions (CI/CD) \\
\textbf{Frameworks:} iOS SDK, Flutter SDK


% ---------- EDUCATION ----------
\section{Education}
\textbf{Master's degree in Computer Science} \hfill 2021\\ 
RGPV University \bull Bhopal, MP \bull GPA: 4.5/5.0

\end{document}