\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Experienced iOS developer adept in Flutter and Swift. Proficient in developing complex native integrations, ensuring day-zero compatibility with latest iOS betas and WWDC updates, and optimizing for startup time, memory usage, and frame rates. Experience in improving overall code quality with Objective-C/Swift based SDK development.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Developed complex native iOS integrations with high fidelity and responsiveness using Flutter.
  \item Proactively tracked WWDC announcements and iOS betas to ensure day-zero compatibility, including new Swift versions.
  \item Profiled and optimized startup time, memory usage and frame rates to match native app performance.
  \item Built a new, dynamic iOS focused UI using advanced Dart features (mixins, factory constructors, detailed enums), improving overall project code quality.
  \item Developed and stabilized multiple CI/CD workflows, reducing build failures by 40\%.
  \item Implemented a unified CI/CD pipeline for Android, iOS, Firebase Distribution, and Shorebird, reducing distribution time by several hours (60-70\%).
  \item Replaced GitHub-hosted runners with local runners, reducing infrastructure costs by 150\% and speeding up builds by 25\%.
\end{itemize}
\vspace{12pt}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Responsible for developing SDKs and making significant contributions to open source projects.
  \item Demonstrated strong skills in iOS performance and memory profiling.
  \item Integrated \textbf{Agora’s} native Android and iOS SDK into a Flutter plugin, enabling seamless whiteboard and networking capabilities while reducing development time by 25\%.
  \item Established a reliable video calling mechanism by integrating FCM, \textbf{iOS CallKit}, and Flutter, delivering functionality on par with WhatsApp.
  \item Developed a \textbf{Flutter video calling plugin} inspired by getstream.io with an abstract ringer for easy Android/iOS integration using native CallKit, cutting development time by over 75\%.
  \item Implemented responsive designs for tablet and iPad, ensuring pixel-perfect UI across diverse screen sizes.
  \item Built a dedicated Flutter app from scratch for tutors, enabling 50,000+ students and tutors to collaborate effectively.
  \item Led revisions and seamless deployment of \textbf{PuStack} and \textbf{PuStack Tutor} apps on \textbf{Play Store} and \textbf{App Store}.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Developed iOS-focused features and ensured smooth functioning of the app by rigorous profiling and debugging.
  \item Ensured seamless UI/UX for the app catering to various device sizes and orientations.
  \item Utilized advanced Dart, Swift and Objective C features for improved performance and code-quality.
  \item Integrated native platform code using Flutter's platform channels to achieve certain features and functionality.
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Developed an SDK/framework for Flutter implementing complex functionality using native integrations.
  \item Contributed to open source projects, ensuring the usage of best practices and maintaining high-quality code.
  \item Ensured device compatibility with latest iOS updates and Swift versions.
\end{itemize}

\org{The CS Guy} \bull Passion Project \bull \href{https://youtube.com/@TheCSGuy}{youtube.com/@TheCSGuy}
\begin{itemize}
  \item Demonstrated advanced state management (Bloc, Riverpod, Provider) and TDD practices.
  \item Developed complex iOS-centric features using Flutter.
  \item Delivered a free Flutter course reaching 150,000+ viewers.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{iOS Development:} Objective-C, Swift, CallKit, Core Data \\
\textbf{Flutter:} Bloc, Navigator 2.0, Provider, Riverpod, Freezed, GetIt, GoRouter, MVVM, Unit Testing\\
\textbf{Mobile:} Android (Java, Kotlin, Jetpack Compose), iOS (Swift) \\
\textbf{Web:} ReactJS, NextJS (TypeScript), ExpressJS, Zustand, Redux \\
\textbf{Backend:} Firebase, MongoDB, Prisma, Supabase, ConvexDB \\
\textbf{Source Control:} Git, GitHub, GitHub Actions (CI/CD)

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}