\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Highly skilled software developer with extensive experience in developing iOS and watchOS applications using Swift. Proficient in Xcode and SwiftUI as well as UIViewController lifecycle. Have a high ability to use MVVM architecture pattern, tuning app performance, and integrating it with REST services. Familiar with managing offline data storage, fetching data from HealthKit, and handling push notifications. Have a track record of conducting rigorous unit/UI testing, CI/CD automation, and managing App Store submission and provisioning processes. Worked in close collaboration with design, product, QA, and firmware teams. Follow strict accessibility, localization, security, and privacy best practices.


% ---------- EXPERIENCE ----------
\section{Experience}
\role{iOS Developer} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Developed high-quality iOS apps using Swift and Xcode.
  \item Worked on app optimization leading to an increase in performance.
  \item Managed the integration with REST services for better data management.
  \item Participated in rigorous UI/Unit testing and CI/CD automation in an Agile workflow.
  \item Collaborated with design, product, QA, and firmware teams for successful app launching.
\end{itemize}
\vspace{12pt}
\role{iOS Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Designed and developed a robust app for iOS devices using Swift and Xcode.
  \item Led the integration with HealthKit and developed push notification functionality.
  \item Played a major role in unit/UI testing and CI/CD automation during app development.
  \item Worked in close coordination with design, product, QA, and firmware teams.
\end{itemize}


% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Worked on this expense tracking app for iOS devices.
  \item Used Swift for development, implementing the concepts of MVC/MVVM architectures.
  \item Incorporated requirements such as offline data storage, integration with REST services and push notifications.
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Created an iOS application, MyMoney, focusing on accessibility, localization, security, and privacy measures.
  \item Worked on performance tuning, UI testing, CI/CD automation, and managing App Store submission and provisioning processes.
  \item Conducted unit/UI testing for the rigorous testing life cycle, ensuring high-quality application development.
\end{itemize}


% ---------- SKILLS ----------
\section{Skills}

\textbf{Languages:} Proficient in Swift, familiar with Objective-C \\
\textbf{Frameworks/Tools:} Xcode, UIKit/SwiftUI \\
\textbf{Architecture Patterns:} MVC, MVVM, Clean \\
\textbf{Testing:} Unit/UI testing, CI/CD automation \\
\textbf{Services:} REST/GraphQL, Bluetooth/HealthKit Integration \\
\textbf{Practices:} Adherence to accessibility, localization, security, and privacy best practices \\
\textbf{Development:} Agile workflows, App Store submission, signing, and provisioning 

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}