\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Firstname Lastname},
  pdfauthor={Firstname Lastname},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Firstname Lastname}\par\vspace{6pt}
    {\color{Primary}
      City, State (Open to relocation) \bull
      \blackLink{mailto:you@email.com}{you@email.com} \bull
      \blackLink{https://github.com/yourhandle}{github.com/yourhandle} \bull
      \blackLink{https://linkedin.com/in/yourhandle}{linkedin.com/in/yourhandle}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty}

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Senior Software Engineer specializing in Rust and systems programming. Proven record delivering low-latency, memory-safe services at scale, leading migrations from C++/Go to Rust, and elevating reliability through rigorous testing, observability, and SRE practices.

% ---------- CORE SKILLS ----------
\section{Core Skills}
\textbf{Languages:} Rust (async, lifetimes, generics, unsafe/FFI), C/C++, Go, Python\\
\textbf{Systems:} Linux, networking, filesystems, IPC, multithreading, performance tuning\\
\textbf{Rust Ecosystem:} Cargo, Tokio, async-std, serde, tonic/gRPC, prost, anyhow/thiserror, tracing, criterion, proptest, quickcheck, libFuzzer/AFL, Clippy, Miri\\
\textbf{Tooling:} Bazel, Git, CI/CD (Buildkite/GitHub Actions), Docker, Kubernetes, OpenTelemetry, Prometheus, Grafana\\
\textbf{Domains:} Distributed systems, microservices, RPC, streaming, storage, security/hardening

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Senior Software Engineer (Rust)} \bull \org{Google} \bull \href{http://www.google.com}{www.google.com} \bull \place{City, State} \hfill MM YYYY -- Present
\begin{itemize}
  \item Led migration of a performance-critical service from C++ to Rust, cutting p99 latency by 35\% and reducing memory-related incidents to zero over 6 months.
  \item Designed and shipped a Rust-based, async RPC proxy (Tokio + tonic) handling >150k RPS with p99 <10 ms under peak load; improved CPU efficiency by 25\% via zero-copy data paths.
  \item Introduced property-based and fuzz testing pipelines (proptest, libFuzzer) uncovering >30 defects pre-production; defined reliability SLOs and on-call practices reducing incident rate by 40\%.
  \item Built observability with OpenTelemetry tracing and Prometheus metrics; reduced mean time to detect by 60\%.
  \item Authored internal Rust guidelines, mentored 8 engineers on ownership/concurrency patterns, and conducted >150 code reviews.
  \item Implemented safe FFI bridges to existing C++ libraries; replaced unsafe blocks with audited abstractions to meet security review requirements.
\end{itemize}

% The "Previous Company" part can be repeated for more employments.

\role{Software Engineer (Rust/C++/Go)} \bull \org{Previous Company} \bull \href{http://www.previouscompany.com}{www.previouscompany.com} \bull \place{City, State} \hfill MM YYYY -- MM YYYY
\begin{itemize}
  \item Implemented high-throughput, fault-tolerant services; introduced async Rust components where latency and safety were critical.
  \item Drove performance profiling (perf/eBPF) and workload benchmarking to guide capacity planning and cost reductions.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}

\org{High-Throughput Stream Processor (Rust)}
\begin{itemize}
  \item Async pipeline using Tokio; backpressure-aware design; achieved 2x throughput vs. prior Go service with stable p99 latency.
\end{itemize}

\org{Secure Config Service (Rust)}
\begin{itemize}
  \item Implemented end-to-end validation, schema evolution, and client-side caching with exponential backoff; zero production regressions over 12 months.
\end{itemize}

% ---------- OPEN SOURCE & COMMUNITY ----------
\section{Open Source \& Community}
Contributor to Rust ecosystem crates (e.g., serde/tracing-adjacent tooling). Presented internal tech talks on async Rust and safe FFI patterns.

% ---------- EDUCATION ----------
\section{Education}
\textbf{B.S. or M.S., Computer Science (or related field)} \bull \org{University Name} \bull \place{City, State} \bull YYYY.

% ---------- CERTIFICATIONS ----------
\section{Certifications}
\textbf{(Linux Performance, Cloud/Kubernetes, or Security credentials if applicable)}

% ---------- KEYWORDS FOR ATS ----------
\section{Keywords for ATS}
Rust, Tokio, async, ownership/borrowing, lifetimes, FFI, C/C++, gRPC, Protobuf, distributed systems, observability, OpenTelemetry, Prometheus, fuzzing, property-based testing, Bazel, Cargo, Linux, performance profiling, SRE, reliability.

\end{document}