\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[a4paper, total={6in, 9in}]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=cyan
}
\begin{document}

\begin{center}
{\LARGE \textbf{Ronak Punase}} \\
Bhopal, Madhya Pradesh, India \\
punase.ronak99@gmail.com \quad +91 86025 59742 \\
\href{https://www.linkedin.com/in/ronak-punase}{LinkedIn: ronak-punase} \quad
\href{https://ronakpunase.dev}{Website: ronakpunase.dev}
\end{center}

\rule{\textwidth}{0.4pt}

\vspace{6pt}
\section*{Professional Summary}
Competitive when learning, collaborative when building. Experienced Software Engineer with a track record of delivering robust software systems and driving architectural decisions. Proficient in C/C++ and Python; comfortable with RTOS and Linux environments; adept at debugging, performance analysis, and ensuring reliability and maintainability. Skilled at shaping technical direction, collaborating with hardware, systems, and product management teams to define requirements and priorities; conducting code reviews, mentoring junior engineers, and improving development processes in Agile settings. Eager to apply to embedded software challenges at Infineon, leveraging a high-trust, collaborative culture and familiarity with software life cycles and automotive safety practices.

\vspace{6pt}
\section*{Experience}
\subsection*{Farmako, Gurugram, Haryana}
\textbf{Software Development Engineer} \hfill 03/2025 -- Present
\begin{itemize}[leftmargin=*]
  \item Led modular software component design and architecture, collaborating with cross-functional teams (hardware, QA, product management) to define requirements and priorities.
  \item Implemented and improved CI/CD pipelines, reducing build failures by 40\% and accelerating feature delivery.
  \item Established coding standards and participated in regular code reviews; mentored junior engineers to improve maintainability and quality.
  \item Implemented instrumentation and testing strategies to improve software quality and reliability; documented progress and outcomes for stakeholders.
  \item Re-engineered critical components for better performance and maintainability; aligned with product roadmaps and platform owners.
\end{itemize}

\subsection*{PuStack, Remote}
\textbf{Flutter Developer} \hfill 07/2021 -- 03/2025
\begin{itemize}[leftmargin=*]
  \item Collaborated with backend, design, and product teams to define requirements for scalable cross-platform mobile apps serving 50{,}000+ users.
  \item Led code reviews, established front-end development standards, and built reusable architectures to improve maintainability and velocity.
  \item Implemented CI/CD workflows and automated testing, reducing release cycle times and improving software quality.
  \item Focused on performance, reliability, and user experience; mentored new developers and contributed to knowledge sharing.
  \item Gained exposure to embedded-like software considerations, portability, and system-level thinking through cross-domain projects and debugging.
\end{itemize}

\vspace{6pt}
\section*{Education}
\textbf{Bachelors of Engineering}, RGPV University, Bhopal, MP \hfill 2021 \\
GPA: 4.25/5.0

\vspace{6pt}
\section*{Technical Skills}
\textbf{Languages:} C, C++, Python \\
\textbf{Embedded/OS:} RTOS (FreeRTOS-like), Linux, cross-platform development \\
\textbf{Tools:} Git, CI/CD, Jira, debugging tools, performance profiling \\
\textbf{Software Lifecycle:} Agile, SDLC, testing, code reviews, documentation \\
\textbf{Safety/Standards:} Familiar with automotive software practices (to align with MISRA/ASPICE as applicable)

\vspace{6pt}
\section*{Projects}
\begin{itemize}[leftmargin=*]
  \item \textit{MyMoney} — Expense tracking app in Flutter; demonstrated ability to deliver maintainable code and scalable architectures; documented design decisions.
  \item \textit{Majestic UI} — Passion project; showcased ability to ship features and engage users; wrote clean, extensible code.
  \item \textit{The CS Guy} — YouTube channel with tutorials; demonstrated communication and teaching ability.
\end{itemize}

\end{document}