\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}
% Template placeholder command - renders [PLACEHOLDER] without monospace font
\newcommand{\placeholder}[1]{\lbrack #1\rbrack}


% ---------- Header ----------
% Header section - replaced with actual contact information
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, Madhya Pradesh, India \bull
      \href{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \href{https://www.linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \href{https://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Results-driven software engineer with strong background in embedded systems, ARM Cortex-M microcontrollers, and C/C++ development. Experienced in defining software architecture, coding standards, and reusable components; adept at system-level design and cross-functional roadmaps. Demonstrates strong collaboration with hardware, firmware, validation, and systems teams; excels in verification planning, debugging, and delivering maintainable documentation. Provides technical leadership and mentoring in Agile/DevOps environments, and actively stays current with industry trends to guide product direction.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill \place{03/2025 -- Present} \\
\org{Farmako} \bull \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Led embedded firmware design and architecture decisions for ARM Cortex-M based devices, delivering modular, reusable components written in C/C++.
  \item Defined coding standards and contributed to system-level design, establishing cross-functional roadmaps with hardware, validation, and systems teams.
  \item Created verification plans and test strategies; implemented unit/integration tests and debugging workflows to ensure software quality across firmware releases.
  \item Produced design/architecture documentation and test plans to support maintainability and knowledge transfer.
  \item Provided technical leadership and mentoring to junior engineers; contributed to team growth and capability development.
  \item Drove Agile/DevOps–style processes; implemented automated build/test pipelines for embedded firmware, improving release velocity and reducing defects.
  \item Stayed current with relevant technologies and industry trends to inform product development and technical direction.
\end{itemize}
\vspace{12pt}

\role{Flutter Developer} \hfill \place{07/2021 -- 03/2025} \\
\org{PuStack} \bull \hfill \place{Remote}
\begin{itemize}
  \item Collaborated with cross-functional teams to design and implement mobile apps (Flutter/Dart) that interface with embedded hardware APIs, emphasizing robust UI/UX and reliable data flows.
  \item Led architecture and code quality decisions for cross-platform applications; established best practices for maintainability and testability.
  \item Implemented CI/CD pipelines and automated testing to shorten release cycles and improve product quality.
  \item Mentored junior developers and conducted code reviews to strengthen team capabilities.
  \item Worked with product and hardware teams to align software deliverables with hardware capabilities and validation plans.
\end{itemize}
\vspace{12pt}

% ---------- PROJECTS ----------
\section{Projects}
\org{MyMoney} \bull \placeholder{Flutter} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Expense tracking app built in Flutter; demonstrated end-to-end mobile UI, data persistence, and synchronization features.
  \item Focus on clean architecture and responsive design to support rapid feature delivery.
\end{itemize}

\org{Majestic UI} \bull \placeholder{UI/UX Project} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Passion project showcasing a reusable UI component library with a focus on performance and accessibility.
  \item Achieved strong audience engagement and practical demonstrations of design-to-code workflows.
\end{itemize}

\org{The CS Guy} \bull \placeholder{YouTube Channel} \bull \href{https://www.youtube.com}{YouTube}
\begin{itemize}
  \item YouTube channel providing Flutter tutorials; built a community around mobile UI development and app architecture concepts.
  \item Created content that emphasized practical software engineering practices and iterative learning.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}
\textbf{Technical:} Embedded Systems, Microcontrollers, ARM Cortex-M, C, C++, Flutter, Dart, Git, CI/CD, System Design \\
\textbf{Mobile/Web:} Flutter, ReactJS, NextJS \\
\textbf{Databases/Back-end:} Firebase, MongoDB, ExpressJS \\
\textbf{Methodologies/Collaboration:} Agile, DevOps, Testing & Verification, Design Reviews, Mentoring, Cross-Functional Communication

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelor of Engineering} \bull \textbf{RGPV University} \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}