\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}
% Template placeholder command - renders [PLACEHOLDER] without monospace font
\newcommand{\placeholder}[1]{\lbrack #1\rbrack}

% ---------- Header ----------
% Header section - replace placeholders with actual contact information
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, Madhya Pradesh, India \bull
      punase.ronak99@gmail.com \bull
      +91 86025 59742 \bull
      \href{https://www.linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \href{https://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Competitive when learning, collaborative when building. Seasoned software engineer with experience across mobile app development (Flutter) and embedded systems (ARM Cortex-M). Proven track record leading design and implementation, architecture decisions, mentoring, and code reviews; driving CI/CD improvements and cross-functional collaboration with hardware, firmware, QA and product management. Committed to delivering secure, reliable software with performance optimizations and system-level thinking, while embracing Infineon's focus on career development, flexible work arrangements, and wellbeing.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill 03/2025 -- Present \\
\org{Farmako} \bull \href{https://example.com/farmako}{Farmako} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Led design and implementation of a component/system across mobile UI, establishing architecture standards and guiding junior engineers through code reviews.
  \item Architected and implemented a design system governed by Figma tokens; ensured consistency across features and reduced UI defects.
  \item Developed dynamic UI using Dart features with a focus on clean architecture and testability.
  \item Built and evolved CI/CD workflows, reducing build failures by 40% and minimizing distribution time; implemented automated quality gates.
  \item Implemented a unified CI/CD pipeline; replaced GitHub runners with local runners, speeding up builds by 25%.
  \item Re-implemented cart as a local-first system, improving UX performance and resilience.
  \item Collaborated with hardware, firmware, QA, and product management to analyze requirements, perform design reviews, and own milestones end-to-end.
\end{itemize}
\vspace{12pt}

\role{Flutter Developer} \hfill 07/2021 -- 03/2025 \\
\org{PuStack} \bull \href{https://example.com/pustack}{PuStack} \hfill \place{Remote}
\begin{itemize}
  \item Integrated Agora’s SDK into a Flutter plugin, reducing development time by 25% and ensuring robust video features.
  \item Established a reliable video calling mechanism using Flutter and native bridges; collaborated with cross-functional teams to define requirements.
  \item Developed a dedicated Flutter app for tutors, enabling collaboration among 50,000+ users; implemented scalable architecture.
  \item Built admin tools on Flutter Web and led app revisions and deployments; conducted code reviews and mentored junior developers.
  \item Designed a resilient call-billing system to improve engagement while maintaining data security and privacy.
  \item Acted as a technical lead on features, performed regular code reviews, and contributed to system-level integration.
  \item Worked with product management to analyze requirements, participate in design reviews, and ensure on-time milestone delivery.
\end{itemize}
\vspace{12pt}

% ---------- PROJECTS ----------
\section{Projects}
\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Flutter-based expense tracking app with local persistence and cloud sync; focused on secure data handling and a responsive UI.
  \item Architected modular UI components and data layer to support rapid feature iteration.
\end{itemize}
\bigskip

\org{Majestic UI} \bull
\href{https://www.youtube.com/@MajesticUI}{YouTube/channel}
\begin{itemize}
  \item UI/UX components library and tutorials; project gained significant audience, driving adoption and feedback loops.
  \item Demonstrated end-to-end design, implementation, and testing of UI patterns in Flutter.
\end{itemize}
\bigskip

\org{The CS Guy} \bull
\href{https://www.youtube.com/@TheCSGuy}{YouTube}
\begin{itemize}
  \item Flutter tutorials and demonstrations; built a community around mobile development concepts and best practices.
\end{itemize}
\vspace{12pt}

% ---------- SKILLS ----------
\section{Skills}
\textbf{Programming Languages:} Dart, C, Java, Kotlin, Swift \\
\textbf{Mobile/Frontend Frameworks:} Flutter, ReactJS, NextJS, ExpressJS \\
\textbf{Embedded & IoT:} Embedded Systems, Microcontrollers, ARM Cortex-M \\
\textbf{Data & Backend:} Firebase, MongoDB \\
\textbf{Design & Architecture:} Software Development Methodologies, System Design, Design Systems \\
\textbf{Tools & Practices:} CI/CD, Git, Agile/Scrum, Code Reviews, Cross-functional collaboration

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelor of Engineering} \bull \textbf{RGPV University} \bull \place{Bhopal, MP} \bull 2021 \bull GPA: 4.25/5.0

\end{document}