\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor} 
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Jeffrey Epstein},
  pdfauthor={Jeffrey Epstein},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Jeffrey Epstein}\par\vspace{6pt}
    {\color{Primary}
      Little St. James, USVI \bull
      \blackLink{mailto:jeffrey.epstein@gmail.com}{jeffrey.epstein@gmail.com} \bull
      Currently Unavailable \bull
      \blackLink{https://linkedin.com/in/jeffrey-epstein}{in/jeffrey-epstein} \bull
      \blackLink{http://jeffreyepstein.dev}{jeffreyepstein.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Highly motivated financier and educator with an exceptional talent for networking with the world's most influential people. Specialized in creating exclusive educational opportunities and managing high-profile client relationships. Proven track record of avoiding accountability through strategic legal maneuvering and maintaining connections in the highest echelons of society. Expert in private island management, flight logistics, and maintaining absolute discretion. Currently seeking new opportunities (pending resolution of certain legal matters).

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Financial Advisor \& Private Island Curator} \hfill 1990s -- 2019 \\
\org{Self-Employed} \bull Various Locations \hfill \place{New York, NY \& US Virgin Islands}
\begin{itemize}
  \item Established and operated a highly exclusive private island resort, specializing in VIP guest services and maintaining absolute privacy for high-net-worth individuals.
  \item Developed innovative recruitment strategies for identifying and engaging talented young individuals for educational and professional development opportunities.
  \item Managed complex logistics operations, including private jet transportation and coordination of international travel for distinguished clientele.
  \item Cultivated relationships with world leaders, royalty, academics, and business magnates, building an unparalleled network of influential contacts.
  \item Successfully negotiated multiple plea deals and legal settlements, demonstrating exceptional skills in crisis management and legal strategy.
  \item Pioneered creative approaches to age verification and documentation processes, ensuring compliance with various international regulations.
\end{itemize}
\vspace{12pt}

\role{Mathematics Teacher} \hfill 1974 -- 1976 \\
\org{Dalton School} \hfill \place{New York, NY}
\begin{itemize}
  \item Taught advanced mathematics to high school students, developing innovative teaching methods that emphasized one-on-one instruction.
  \item Recognized for exceptional ability to connect with students and create personalized learning experiences outside traditional classroom settings.
  \item Left position to pursue more lucrative opportunities in finance (and, allegedly, other ventures that don't look great on a resume).
\end{itemize}
\vspace{12pt}

\role{Options Trader} \hfill 1976 -- 1981 \\
\org{Bear Stearns} \hfill \place{New York, NY}
\begin{itemize}
  \item Rapidly promoted from options trader to limited partner, demonstrating exceptional performance in high-stakes financial markets.
  \item Developed expertise in identifying undervalued assets and creating complex financial structures (skills that would later prove useful in other contexts).
  \item Built reputation for aggressive trading strategies and willingness to push boundaries in pursuit of profit.
\end{itemize}

% ---------- NOTABLE ACHIEVEMENTS ----------
\section{Notable Achievements}
\role{Founder \& Director} \hfill 1998 -- 2019 \\
\org{Jeffrey Epstein VI Foundation} \hfill \place{US Virgin Islands}
\begin{itemize}
  \item Established charitable foundation focused on science education and research, demonstrating commitment to advancing human knowledge (and, coincidentally, providing tax benefits).
  \item Hosted exclusive scientific conferences and gatherings, bringing together Nobel laureates, academics, and other distinguished guests at private island facilities.
  \item Successfully maintained foundation operations despite multiple legal challenges and public scrutiny, showcasing resilience and determination.
\end{itemize}
\vspace{12pt}

\role{Aviation Enthusiast} \hfill 1990s -- 2019 \\
\org{Private Air Travel Services} \hfill \place{International}
\begin{itemize}
  \item Operated private aircraft fleet, including the infamous ``Lolita Express,'' providing convenient transportation for VIP clients and associates.
  \item Developed expertise in international flight planning and customs procedures across multiple jurisdictions.
  \item Maintained impeccable safety record (at least, no crashes—can't speak to other safety metrics).
\end{itemize}

% ---------- LEGAL EXPERTISE ----------
\section{Legal Expertise}
\role{Defendant \& Legal Strategist} \hfill 2005 -- 2019 \\
\org{Various Court Systems} \hfill \place{Florida, New York, USVI}
\begin{itemize}
  \item Successfully negotiated controversial 2008 plea deal, avoiding federal prosecution through strategic legal representation and creative interpretation of ``non-prosecution agreement'' terms.
  \item Demonstrated exceptional ability to serve minimal jail time (13 months, mostly on work release) despite serious charges, showcasing mastery of legal system navigation.
  \item Maintained operations and reputation despite public allegations and media scrutiny, proving that with the right connections, consequences can be remarkably flexible.
  \item Currently: Status pending (last known location: Metropolitan Correctional Center, NYC—though that situation didn't end well either).
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Networking:} Building relationships with billionaires, world leaders, royalty, and academic elites; maintaining connections across multiple industries and social circles\\
\textbf{Legal Strategy:} Negotiating plea deals, avoiding prosecution, managing crisis communications, and leveraging legal loopholes\\
\textbf{Operations Management:} Private island administration, staff coordination, security protocols, and maintaining absolute discretion\\
\textbf{Aviation:} Private jet operations, international flight planning, customs navigation, and VIP transportation logistics\\
\textbf{Finance:} Options trading, asset management, tax optimization strategies, and creative financial structuring\\
\textbf{Education:} Mathematics instruction, curriculum development, and ``alternative'' educational program design\\
\textbf{Technology:} Surveillance systems, security infrastructure, and maintaining comprehensive documentation (allegedly)

% ---------- EDUCATION ----------
\section{Education}
\textbf{Attended} \bull Cooper Union \bull New York, NY \bull 1969 -- 1971 (Did not graduate—too busy pursuing other interests)\\
\textbf{Attended} \bull Courant Institute of Mathematical Sciences, NYU \bull New York, NY \bull 1971 -- 1972 (Also did not graduate—apparently higher education wasn't the priority)\\
\textbf{High School Diploma} \bull Lafayette High School \bull Brooklyn, NY \bull 1966

\vspace{12pt}
\textit{Note: Formal education clearly wasn't necessary for building a network of powerful friends and accumulating significant wealth. Sometimes, ambition and questionable ethics are all you need!}

\end{document}