\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Sarah Johnson},
  pdfauthor={Sarah Johnson},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}
\newcommand{\placeholder}[1]{\lbrack #1\rbrack}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Sarah Johnson}\par\vspace{6pt}
    {\color{Primary}
      Austin, Texas, USA \bull
      \blackLink{mailto:sarah.johnson@email.com}{sarah.johnson@email.com} \bull
      +1-555-987-6543 \bull
      \blackLink{https://linkedin.com/in/sarahjohnson}{linkedin.com/in/sarahjohnson} \bull
      \blackLink{https://github.com/sarahjohnson}{github.com/sarahjohnson}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty}

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Accomplished technical leader and engineer with 6+ years working at the intersection of product, engineering, and AI infrastructure. Hands-on experience building and scaling end-to-end systems, driving innovative solutions for complex domains such as payments, cloud platforms, and AI integrations. Adept at setting technical vision and collaborating cross-functionally in fast-paced, ambiguous startup environments.

% ---------- EXPERIENCE ----------
\section{Experience}

\role{Senior Product Manager} \hfill 03/2021 -- Present \\
\org{Microsoft} \bull \href{https://microsoft.com}{microsoft.com} \hfill \place{Redmond, WA}
\begin{itemize}
  \item Spearheaded the technical vision and system design for Azure DevOps, architecting scalable integrations and growing enterprise adoption by \textbf{35\%}.
  \item Led cross-functional teams of 12+ engineers \& designers to deliver high-impact platform features, generating \textbf{\$2M+} in annual revenue.
  \item Drove AI-powered enhancements and automation across developer workflows, collaborating with internal AI and infrastructure teams.
  \item Championed payment and billing feature initiatives, collaborating with finance and engineering to streamline platform monetization.
  \item Implemented robust OKR-driven processes, increasing technical team alignment and velocity by \textbf{50\%}.
  \item Partnered with founders and product executives to define roadmap, frequently representing engineering in strategic customer and sales discussions.
\end{itemize}
\vspace{12pt}

\role{Product Manager} \hfill 06/2018 -- 02/2021 \\
\org{Amazon} \bull \href{https://amazon.com}{amazon.com} \hfill \place{Seattle, WA}
\begin{itemize}
  \item Owned backend product lifecycle for scalable seller tools platform, supporting \textbf{100K+} merchants and integrating with payment \& infrastructure systems.
  \item Designed and implemented metrics dashboards using \textbf{SQL, Mixpanel, and Amplitude} for data-driven product and engineering insights.
  \item Led efforts to optimize API reliability and automate support, reducing customer support tickets by \textbf{25\%}.
  \item Drove user-focused UX improvements, boosting satisfaction from 3.2 to \textbf{4.5 stars} while ensuring stability at scale.
  \item Regularly collaborated with engineering, infrastructure, and payment teams across multiple time zones to launch critical features.
  \item Presented technical vision and platform updates to VP-level stakeholders and participated in technical review sessions with cross-functional teams.
\end{itemize}
\vspace{12pt}

% ---------- DYNAMIC SECTION 1 ----------
\section{Technical Skills}
\textbf{Programming \& Data:} SQL, Python, API Design, Data Analysis, Cloud Infrastructure (Azure, AWS) \\
\textbf{AI \& Product:} AI Integrations, A/B Testing, Product Analytics (Mixpanel, Amplitude, Google Analytics) \\
\textbf{Frameworks \& Tools:} Agile/Scrum, Jira, Confluence, Asana, Wireframing (Figma, Sketch) \\
\textbf{Other:} Payments Integration, System Design, Stakeholder Management, English (Native), Spanish (Conversational) \\

% ---------- DYNAMIC SECTION 2 ----------
\section{Key Projects \& Awards}
\org{Internal Prioritization Tool} \bull Internal Platform \\
\begin{itemize}
  \item Built and deployed an internal tool for product decisioning, now used by \textbf{50+} PMs, engineering, and sales to drive velocity in high-growth environments.
\end{itemize}
\org{Open-Source Management Framework} \bull Open Source \bull \href{https://github.com/sarahjohnson}{github.com/sarahjohnson} \\
\begin{itemize}
  \item Created a product management framework with \textbf{1,000+ GitHub stars}, supporting community-driven innovation for modern product and engineering teams.
\end{itemize}
\textbf{Product Manager of the Year} \bull Microsoft \bull 2023 \\
\textbf{Innovation Award} \bull Amazon \bull 2020

% ---------- EDUCATION ----------
\section{Education}
\textbf{MBA in Technology Management} \bull Stanford Graduate School of Business \bull Stanford, CA \bull 2018 \bull GPA: 3.9/4.0 \\
Dean's List, Product Management Fellowship

\vspace{6pt}

\textbf{B.S. in Computer Science} \bull University of Texas at Austin \bull Austin, TX \bull 2016 \bull GPA: 3.7/4.0

\end{document}