\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Sarah Johnson},
  pdfauthor={Sarah Johnson},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}
\newcommand{\placeholder}[1]{\lbrack #1\rbrack}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Sarah Johnson}\par\vspace{6pt}
    {\color{Primary}
      Austin, Texas, USA \bull
      \blackLink{mailto:sarah.johnson@email.com}{sarah.johnson@email.com} \bull
      +1-555-987-6543 \bull
      \blackLink{https://linkedin.com/in/sarahjohnson}{linkedin.com/in/sarahjohnson} \bull
      \blackLink{https://github.com/sarahjohnson}{github.com/sarahjohnson}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty}

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Experienced founding engineer and product leader with 6+ years delivering scalable, user-centric and data-driven technology solutions across AI, payments, and developer infrastructure domains. Proven ability to architect systems, integrate with third-party services, and drive growth by collaborating with founders, engineering, product, and go-to-market teams. Hands-on with AI and payments technologies, passionate about solving high-impact, ambiguous problems at early-stage startups.

% ---------- EXPERIENCE ----------
\section{Experience}

\role{Senior Product Manager \& Technical Lead} \hfill 03/2021 -- Present \\
\org{Microsoft} \bull \href{https://microsoft.com}{microsoft.com} \hfill \place{Redmond, WA}
\begin{itemize}
  \item Led product and technical strategy for Azure DevOps integrations, driving a 35\% increase in enterprise adoption with a focus on developer tooling and scalable cloud infrastructure.
  \item Directed a cross-functional team of 12 engineers and designers to deliver AI-powered features supporting automation, user analytics, and workflow optimization. 
  \item Spearheaded integrations with leading AI providers and payment platforms, enabling secure and scalable processing of transactions and intelligent user experiences.
  \item Collaborated closely with founders, sales, and customers to define product vision and join high-value sales development calls as technical stakeholder.
  \item Introduced and scaled an OKR framework that improved engineering team alignment by 50\%, establishing culture and processes tailored for a rapid-growth environment.
  \item Shipped 3 large-scale features generating \$2M+ in annual revenue, directly contributing to company growth and user engagement.
\end{itemize}
\vspace{12pt}

\role{Product Manager (Full Stack Engineering)} \hfill 06/2018 -- 02/2021 \\
\org{Amazon} \bull \href{https://amazon.com}{amazon.com} \hfill \place{Seattle, WA}
\begin{itemize}
  \item Owned end-to-end lifecycle for seller tools serving 100K+ merchants, driving substantial improvements in platform reliability and payments infrastructure.
  \item Collaborated with engineering to design and deliver robust APIs, backend services, and integrations with fintech/payment systems for high-volume, mission-critical applications.
  \item Leveraged product analytics and SQL to identify opportunities for AI-enabled automation, reducing support tickets by 25\% and boosting seller satisfaction from 3.2 to 4.5 stars.
  \item Coordinated development sprints across global teams, incorporating feedback from direct user research and co-leading stakeholder demo calls.
  \item Presented technical and commercial strategy to VP-level leadership, informing roadmap for scalable revenue-driving features.
\end{itemize}
\vspace{12pt}

% ---------- DYNAMIC SECTION 1 ----------
\section{Key Skills}

\textbf{Technical:} System Architecture, Backend Development, Full Stack Engineering, API Design \& Documentation, Payment Systems Integration, AI Product Integration, Cloud Infrastructure (Azure, AWS), SQL, Product Analytics (Mixpanel, Amplitude, Google Analytics), Agile/Scrum, A/B Testing \& Experimentation \\
\textbf{Developer Tools:} Jira, Confluence, Asana, Figma, Sketch \\
\textbf{Collaboration:} Technical Leadership, Cross-functional Team Building, Stakeholder Management, Go-to-Market Collaboration

% ---------- DYNAMIC SECTION 2 ----------
\section{Awards \& Certifications}

\textbf{Product Manager of the Year} \bull Microsoft \bull 2023 \\
\textbf{Innovation Award} \bull Amazon \bull 2020 \\
\textbf{Certified Scrum Product Owner (CSPO)} \bull Scrum Alliance \bull 2019 \\
\textbf{Google Analytics Individual Qualification} \bull Google \bull 2018

% ---------- EDUCATION ----------
\section{Education}

\textbf{MBA in Technology Management} \bull Stanford Graduate School of Business \bull Stanford, CA \bull 2018 \bull GPA: 3.9/4.0 \\
Dean's List, Product Management Fellowship

\vspace{8pt}

\textbf{B.S. in Computer Science} \bull University of Texas at Austin \bull Austin, TX \bull 2016 \bull GPA: 3.7/4.0

\end{document}