\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Sarah Johnson},
  pdfauthor={Sarah Johnson},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}
\newcommand{\placeholder}[1]{\lbrack #1\rbrack}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Sarah Johnson}\par\vspace{6pt}
    {\color{Primary}
      Austin, Texas, USA \bull
      \blackLink{mailto:sarah.johnson@email.com}{sarah.johnson@email.com} \bull
      +1-555-987-6543 \bull
      \blackLink{https://linkedin.com/in/sarahjohnson}{linkedin.com/in/sarahjohnson} \bull
      \blackLink{https://github.com/sarahjohnson}{github.com/sarahjohnson}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty}

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Seasoned full-stack engineering leader with 6+ years of experience architecting, scaling, and launching cutting-edge products at the intersection of AI, payments, and developer infrastructure. Proven ability to drive technical direction, collaborate directly with founders and cross-functional stakeholders, and execute rapid iteration in fast-paced environments. Extensive background in system design, backend engineering, and AI tool integration; passionate about building culture and processes from the ground up at high-growth startups.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Senior Product Manager \& Technical Lead} \hfill 03/2021 -- Present \\
\org{Microsoft} \bull \href{https://azure.microsoft.com}{azure.microsoft.com} \hfill \place{Redmond, WA}
\begin{itemize}
  \item Directed architecture and development of enterprise-scale \textbf{AI-driven developer tools} on the Azure platform, driving a \textbf{35\%} increase in adoption by Fortune 500 clients.
  \item Led integrations with payment systems and core infrastructure services, enabling seamless \textbf{APIs for external partners} and accelerating new revenue channels.
  \item Managed and mentored a cross-functional team of 12+ engineers and designers to deliver resilient, production-grade features with system reliability exceeding \textbf{99.99\% uptime}.
  \item Drove customer discovery sessions with 200+ users, translated insights into technical requirements, and iterated rapidly to align solutions with evolving market needs.
  \item Collaborated with founders, product, and sales teams to set roadmap, participate in customer calls, and shape technical vision and execution.
  \item Championed data-driven experimentation and rapid prototyping, launching 3+ high-impact features that generated over \$2M in annual revenue.
\end{itemize}
\vspace{12pt}

\role{Product Manager, Developer Platforms} \hfill 06/2018 -- 02/2021 \\
\org{Amazon} \bull \href{https://amazon.com}{amazon.com} \hfill \place{Seattle, WA}
\begin{itemize}
  \item Drove end-to-end delivery of scalable tools powering 100K+ e-commerce sellers, optimizing \textbf{payments infrastructure} and API connectivity.
  \item Designed and implemented backend services leveraging \textbf{AI models} and analytics for fraud detection, boosting onboarding speed by 25\%.
  \item Collaborated with engineering and sales teams across three time zones, ensuring system scalability and compliance for high-volume financial transactions.
  \item Introduced new developer features and integrations, raising seller satisfaction scores from 3.2 to 4.5 stars.
  \item Reduced support tickets by 25\% through improved workflow automation and intuitive UX design.
  \item Regularly presented product and technical roadmaps to C-suite and VP-level stakeholders, aligning on key architecture decisions.
\end{itemize}
\vspace{12pt}

% ---------- DYNAMIC SECTION 1 ----------
\section{Key Skills}
\textbf{Programming:} SQL, Python, JavaScript, API Design, Backend Architecture \\
\textbf{AI Tools:} Integration with OpenAI, Azure Cognitive Services, Experimentation Frameworks\\
\textbf{Payments \& Infrastructure:} Payments API Integrations, Financial Data Engineering, Platform Security\\
\textbf{Developer Tooling:} Mixpanel, Amplitude, Figma, Jira, Agile/Scrum\\
\textbf{Leadership:} Technical Direction, Cross-functional Team Leadership, Stakeholder Engagement

% ---------- DYNAMIC SECTION 2 ----------
\section{Notable Projects \& Recognition}
\org{Internal AI-Powered Product Prioritization Tool} \bull Microsoft \\
\begin{itemize}
  \item Designed and built an internal platform that leverages \textbf{AI-driven analytics} to optimize product roadmaps, adopted by 50+ PMs across Microsoft.
\end{itemize}
\org{Open-Source Product Management Framework} \bull Independent \bull \href{https://github.com/sarahjohnson}{github.com/sarahjohnson} \\
\begin{itemize}
  \item Created and launched an open-source framework with \textbf{1,000+ GitHub stars}, driving adoption among product and engineering leaders.
\end{itemize}
\textbf{Awards:} Product Manager of the Year (Microsoft, 2023), Innovation Award (Amazon, 2020)

% ---------- EDUCATION ----------
\section{Education}
\textbf{MBA in Technology Management} \bull Stanford Graduate School of Business \bull Stanford, CA \bull 2018 \bull GPA: 3.9/4.0

\textbf{B.S. in Computer Science} \bull University of Texas at Austin \bull Austin, TX \bull 2016 \bull GPA: 3.7/4.0

\end{document}