\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Sarah Johnson},
  pdfauthor={Sarah Johnson},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}
\newcommand{\placeholder}[1]{\lbrack #1\rbrack}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Sarah Johnson}\par\vspace{6pt}
    {\color{Primary}
      Austin, Texas, USA \bull
      \blackLink{mailto:sarah.johnson@email.com}{sarah.johnson@email.com} \bull
      +1-555-987-6543 \bull
      \blackLink{https://linkedin.com/in/sarahjohnson}{linkedin.com/in/sarahjohnson} \bull
      \blackLink{https://github.com/sarahjohnson}{github.com/sarahjohnson}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty}


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Engineering leader with 6+ years of experience architecting and delivering full-stack products at scale, bridging the gap between technical teams and business needs. Proven record in designing robust infrastructures, integrating AI-driven features, and driving revenue growth through product and engineering excellence. Skilled in collaborating with founders and cross-functional partners to define technical direction and build culture for high-impact startups.

% ---------- EXPERIENCE ----------
\section{Experience}

\role{Senior Product Manager / Engineering Lead} \hfill 03/2021 -- Present \\
\org{Microsoft} \bull \href{https://azure.microsoft.com}{azure.microsoft.com} \hfill \place{Redmond, WA}
\begin{itemize}
  \item Directed architecture and end-to-end delivery for \textbf{Azure DevOps}, driving a \textbf{35\% increase} in enterprise adoption and supporting \textbf{100K+} users worldwide.
  \item Collaborated with founders and leadership to set roadmap and make key technical decisions for large-scale cloud platforms and developer tooling.
  \item Spearheaded integration of \textbf{AI-powered analytics} and CI/CD automation, improving deployment velocity and user experience.
  \item Led a cross-functional team of 12 engineers and designers in building scalable backend services with robust APIs and infrastructure.
  \item Partnered with sales and product to represent engineering in client meetings, translating customer needs into technical solutions.
  \item Launched features generating \$2M in additional annual revenue, directly impacting Microsoft’s payment and billing systems.
  \item Introduced OKR processes that increased team alignment by 50\% and accelerated product timelines.
\end{itemize}
\vspace{12pt}

\role{Product Manager / Software Engineer} \hfill 06/2018 -- 02/2021 \\
\org{Amazon} \bull \href{https://amazon.com}{amazon.com} \hfill \place{Seattle, WA}
\begin{itemize}
  \item Owned system design and implementation for seller infrastructure tools, serving \textbf{100K+} merchants and handling \textbf{millions of payment transactions} monthly.
  \item Developed and integrated AI-driven recommendation engines to personalize seller experiences and optimize payment flows.
  \item Built and maintained backend services (microservices architecture) using AWS, enabling resilient and scalable infrastructure.
  \item Reduced support tickets by 25\% by implementing data-driven UX improvements across payment and onboarding journeys.
  \item Frequently joined customer and sales calls, aligning technical roadmap with direct merchant feedback and market insights.
  \item Increased seller satisfaction from 3.2 to 4.5 stars and presented business reviews to VP-level executives.
\end{itemize}
\vspace{12pt}

% ---------- DYNAMIC SECTION 1 ----------
\section{Technical Skills}
\textbf{Programming:} Python, SQL, JavaScript, REST APIs, AWS, Azure, Microservices, Infrastructure as Code \\
\textbf{AI/ML:} AI integrations, Product Analytics (Mixpanel, Amplitude, Google Analytics), Experimentation (A/B Testing) \\
\textbf{Product/Process:} Agile/Scrum, System Design, API Design, Wireframing (Figma, Sketch), Payments Integration, Stakeholder Management

% ---------- DYNAMIC SECTION 2 ----------
\section{Selected Projects \& Awards}
\org{Internal Product Prioritization Tool} \bull Microsoft \bull 2022 \\
\begin{itemize}
   \item Architected and built an internal platform enabling 50+ PMs to prioritize features using data-driven signals, accelerating decision-making across teams.
\end{itemize}
\org{Open-Source Product Management Framework} \bull GitHub \bull 2021 \\
\begin{itemize}
   \item Designed and launched a framework for product teams, earning \textbf{1,000+ GitHub stars} in its first year and adopted by global product communities.
\end{itemize}
\vspace{5pt}
\textbf{Product Manager of the Year} \bull Microsoft \bull 2023 \\
\textbf{Innovation Award} \bull Amazon \bull 2020 \\
\textbf{Certified Scrum Product Owner}, Google Analytics Individual Qualification

% ---------- EDUCATION ----------
\section{Education}
\textbf{MBA in Technology Management} \bull Stanford Graduate School of Business \bull Stanford, CA \bull 2018 \bull GPA: 3.9/4.0 \\
\textbf{B.S. in Computer Science} \bull University of Texas at Austin \bull Austin, TX \bull 2016 \bull GPA: 3.7/4.0

\end{document}