\documentclass[10pt, letterpaper]{article}


% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{https://github.com/RonakPunase}{github.com/RonakPunase}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}

I am an accomplished software engineer specializing in machine learning (ML) and application development. My expertise in ML methodologies, programming languages like Python/JavaScript, MVC framework, and data mining techniques has been honed over 6+ years of professional work experience and academic learning. I have a track record of building innovative and high-quality applications and implementing modern user interfaces that follow best practices. Collaborative, resilient, and technically sound, I am ready to work in a challenging role that fosters learning and creativity.

% ---------- EXPERIENCE ----------
\section{Experience}

\role{Senior Software Engineer} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
    \item Integrated machine learning techniques into application development, improving user experience.
    \item Engaged cross-functionally with product, design, ops, and infra teams to build innovative applications and experiences.
    \item Engineered efficient, scalable systems, establishing end-to-end ownership of components/features.
\end{itemize}
\vspace{12pt}
\role{Lead Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
    \item Led complex technical/product efforts and provided technical guidance to peers, ensuring best practices and efficient workflows.
    \item Demonstrated coding proficiency in Java, Java Script, Swift, Python and other technologies.
    \item Showcased ability to drive consensus and determine technical direction.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
    \item Implemented ML algorithms and models on a large scale, attaining measurable business impact.
    \item Achieved real-time pattern recognition, recommendation systems, and data mining capabilities.
    \item Assured code scalability, efficiency, and high performance, identifying and fixing performance issues.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{ML:} Pattern Recognition, Data Mining, AI \\
\textbf{Programming:} C/C++, Java, Python, JavaScript \\
\textbf{Frameworks:} PyTorch, TensorFlow \\
\textbf{Software Engineering:} API Design, Unit Testing, Code Review, Quality Improvement

% ---------- EDUCATION ----------
\section{Education}
\textbf{PhD in Computer Science} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}
