\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/, 
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}  
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{% 
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Dedicated educator with over 5 years of teaching experience. Proven track record in supervising and mentoring teachers, designing assessment strategies, and fostering student success. Strong collaborator in curriculum development and discipline management.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Academic Coordinator} \hfill March 2023 -- Present \\
\org{XYZ Academy} \bull\href{https://xyzacademy.com}{xyzacademy.com} \hfill \place{Bhopal, India}
\begin{itemize}
  \item Supervised and assisted a team of 10 teachers, promoting best practices in student assessment and engagement.
  \item Developed and implemented comprehensive assessment strategies, enhancing the measurement of student outcomes by 30\%.
  \item Collaborated with stakeholders to design and innovate curriculum aligned with state standards.
  \item Monitored student progress meticulously, providing targeted support and intervention strategies.
  \item Maintained classroom discipline, fostering a positive learning environment conducive to academic success.
\end{itemize}
\vspace{12pt}
\role{Teacher} \hfill June 2018 -- March 2023 \\
\org{ABC School} \bull\href{https://abcschool.com}{abcschool.com} \hfill \place{Bhopal, India}
\begin{itemize}
  \item Taught various subjects to middle and high school students, adapting lessons to meet diverse learning styles.
  \item Engaged students through project-based learning and innovative teaching methodologies, resulting in increased student retention by 20\%.
  \item Developed and monitored personalized learning plans for students needing additional support, improving their academic results and confidence.
  \item Actively participated in curriculum review committees to refine and update teaching materials.
  \item Built positive relationships with students, parents, and the community to enhance school culture and student success.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}
\org{Student Performance App} \bull \href{https://studentperformance.xyz}{studentperformance.xyz}
\begin{itemize}
  \item Developed a comprehensive app to track student grades, attendance, and feedback, boosting parent-teacher communication.
  \item Utilized user-friendly designs to create an engaging interface for students and teachers.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}
\textbf{Educational Strategies:} Assessment Design, Curriculum Development, Classroom Management, Teacher Mentoring \newline
\textbf{Technical:} Microsoft Office Suite, Google Suite, Learning Management Systems (LMS) \newline
\textbf{Interpersonal:} Leadership, Communication, Collaboration, Problem Solving

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Education} \bull RGPV University \bull Bhopal, MP \bull 2018 \bull GPA: 4.25/5.0

\end{document}