\documentclass[10pt,letterpaper]{article}

% ---------- Preamble ----------
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontspec}
\setmainfont{Arial}

% ---------- Formatting ----------
\titlespacing*{\section}{0pt}{6pt}{6pt}
\setlist[itemize]{noitemsep, leftmargin=0.6in}

% ---------- Document ----------
\begin{document}

\begin{center}
  {\LARGE \textbf{Ronak Punase}} \\
  \vspace{6pt}
  Bhopal, Madhya Pradesh, India \\
  \href{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \textbar\ +91 86025 59742 \textbar\ \href{https://www.linkedin.com/in/ronak-punase}{LinkedIn: linkedin.com/in/ronak-punase} \textbar\ \href{https://ronak99.github.io/portfolio/}{Portfolio: ronak99.github.io/portfolio/}
\end{center}

\vspace{6pt}

\section*{Summary}
Backend-focused software engineer with 4 years of experience delivering production-grade services. Proven ability to design scalable RESTful APIs, work with MongoDB and ORM tooling (Prisma), and ship features end-to-end for mobile and web clients. Strong collaborator across product, engineering, and operations, with a track record of improving delivery velocity and reliability. Eager to contribute to AI-enabled cloud services and Redis-backed architectures in a fast-paced, hybrid environment.

\section*{Experience}
\textbf{Flutter Developer} \hfill 07/2021 -- Present \\
PuStack, Panipat, Haryana
\begin{itemize}
  \item Built and maintained backend APIs using Node.js/Express, integrated with MongoDB via Prisma to power Flutter mobile apps; enabled reliable data access and scalable endpoints.
  \item Integrated native SDKs and backend services to extend app capabilities, improving feature delivery speed and developer efficiency.
  \item Developed a Flutter video calling plugin, reducing development time for complex features by over 75\%, and implemented a call billing infrastructure to boost instructor engagement by 25\%.
  \item Improved app reliability and performance through careful API design, error handling, and lightweight testing strategies.
\end{itemize}

\section*{Key Projects}
\begin{itemize}
  \item \textbf{Flutter Video Calling Plugin} \hfill 2022
  \begin{itemize}
    \item Led the development of a video calling plugin for Flutter, enabling feature parity with leading messaging apps and accelerating feature rollouts by 75\%.
  \end{itemize}
  \item \textbf{Backend API for PuStack Mobile Apps} \hfill 2021--2023
  \begin{itemize}
    \item Designed and implemented Node.js/Express APIs with MongoDB (via Prisma) to power mobile experiences; delivered secure authentication, data synchronization, and scalable data access.
  \end{itemize}
\end{itemize}

\section*{Skills}
\textbf{Backend & Databases:} Node.js, ExpressJS, MongoDB, Prisma \\
\textbf{Languages & Frameworks:} JavaScript, TypeScript, Dart, Kotlin (basic) \\
\textbf{Web & Mobile:} ReactJS, NextJS, Flutter, Android (Java/Kotlin), iOS (Swift) \\
\textbf{Cloud & Services:} Firebase, Supabase \\
\textbf{DevOps & Tools:} GitHub Actions (familiar), RESTful API design, API testing

\section*{Education}
\textbf{Bachelor of Engineering} \hfill 2021 \\
RGPV University, Bhopal, MP

\end{document}