
\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
% Replace CANDIDATE_NAME with actual name
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}
\newcommand{\placeholder}[1]{\lbrack #1\rbrack}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, Madhya Pradesh, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{https://ronak99.github.io/portfolio/}{ronak99.github.io/portfolio}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Dynamic backend developer with 4 years of experience, excelling in designing and deploying scalable and high-performance applications. Proficient in a range of programming languages and cloud technologies, bringing a strong focus on AI-driven solutions and cross-team collaboration.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Flutter Developer} \hfill 07/2021 -- Present \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Panipat, Haryana}
\begin{itemize}
  \item Developed and deployed scalable mobile applications while ensuring high user engagement and reliable performance, resulting in a \textbf{25\% increase} in instructor use.
  \item Integrated native SDKs and enhanced user experience through responsive designs, significantly improving application performance.
  \item Led the creation of an in-house video calling plugin, leveraging CI/CD practices for seamless deployment across environments.
  \item Mentored team members on best practices in mobile development, sharing knowledge as a content creator on platforms like YouTube.
\end{itemize}
\vspace{12pt}

% ---------- DYNAMIC SECTION 1 (OPTIONAL) ----------
\section{Projects}
\org{Majestic UI} \bull UI Development \bull \href{https://github.com/ronak99/majestic-ui}{GitHub} 
\begin{itemize}
  \item Designed a Flutter UI system with reusable components to enhance development efficiency across projects.
\end{itemize}

\org{Skype Clone in Flutter} \bull Application Development \bull \href{https://github.com/ronak99/skype-clone}{GitHub}
\begin{itemize}
  \item Created a scalable application that mimicked core functionalities of Skype, demonstrating technical prowess in real-time communication.
\end{itemize}

% ---------- DYNAMIC SECTION 2 (OPTIONAL) ----------
\section{Skills}
\textbf{Languages:} Java, Kotlin, Python, Golang, Dart \\
\textbf{Frameworks & Tools:} Flutter, ReactJS, NextJS, Docker, Kubernetes, Terraform, GitHub Actions \\
\textbf{Databases:} Redis, NoSQL \\
\textbf{Concepts:} AI/ML fundamentals, cloud-native applications

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/4.5

\end{document}
