\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}
\newcommand{\placeholder}[1]{\lbrack #1\rbrack}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, Madhya Pradesh, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{https://ronak99.github.io/portfolio/}{ronak99.github.io/portfolio/}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty}

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Experienced backend engineer with 4+ years in designing, developing, testing, and deploying scalable cloud-based solutions across diverse platforms. Expertise in building high-quality production-grade APIs, collaborating on cross-functional teams, and driving innovation with modern languages and cloud-native technologies. Adept at integrating AI/ML capabilities and database architecture, with a passion for delivering robust, reliable, and performant backend services in fast-paced environments.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Backend Software Engineer (Flutter \& Platform)} \hfill 07/2021 -- Present \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Panipat, Haryana, India}
\begin{itemize}
  \item Designed, implemented, and deployed scalable backend APIs powering real-time video and chat features, supporting thousands of concurrent users with high availability.
  \item Integrated and maintained multiple databases including NoSQL solutions, optimizing data models and query performance for rapid, reliable production deployments.
  \item Led cloud-native application initiatives using containerization and CI/CD pipelines (\textbf{GitHub Actions}, Docker), automating testing, delivery, and infrastructure changes.
  \item Collaborated cross-functionally with engineering, DevOps, and product teams to deliver new features, ensure uptime, and drive continuous system improvements.
  \item Orchestrated deployment workflows with \textbf{Kubernetes}, enabling seamless rollouts and real-time monitoring of microservices.
  \item Developed and maintained native SDK integrations (e.g., video platforms), increasing platform engagement by 25\% and enhancing developer productivity through automation.
  \item Researched, prototyped, and incorporated AI/ML-powered experiences (recommendations, chat assistants) leveraging frameworks such as \textbf{TensorFlow} and \textbf{LangChain}.
  \item Championed high standards for code quality, mentoring junior engineers and facilitating knowledge sharing to elevate team capabilities.
\end{itemize}
\vspace{12pt}

% ---------- DYNAMIC SECTION 1 ----------
\section{Key Projects}
\org{Majestic UI} \bull Open Source \bull \href{https://github.com/ronak99/majestic-ui}{github.com/ronak99/majestic-ui}
\begin{itemize}
  \item Architected a reusable UI library for rapid product development in Flutter, leveraging modular design, theming, and maintainability best practices.
\end{itemize}

\org{Skype Clone in Flutter} \bull Production Prototype
\begin{itemize}
  \item Engineered a scalable video calling application with cloud backend, robust API layer, and seamless integration of native SDKs.
\end{itemize}

\org{Inquirely} \bull AI Chatbot System
\begin{itemize}
  \item Developed a custom AI-powered chat assistant backed by \textbf{LangChain} and API microservices, supporting conversational queries and real-time assistance.
\end{itemize}

% ---------- DYNAMIC SECTION 2 ----------
\section{Technical Skills}
\textbf{Languages:} Python, Kotlin, Java, Go, Swift, Dart \\
\textbf{Frameworks:} TensorFlow, LangChain, Node.js, Flutter, ReactJS, Next.js \\
\textbf{Databases:} Redis, MongoDB, PostgreSQL, Firebase \\
\textbf{DevOps:} Docker, Kubernetes, GitHub Actions, Terraform \\
\textbf{Cloud:} Cloud-native development and deployment, CI/CD, Automated testing \\
\textbf{Other:} API Design, Microservices, Scalable systems, AI/ML Integration

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}