\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=0.6in]{geometry}
\usepackage{fontspec}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{4pt}{%
    \large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-6pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{1pt}
\setlength{\topsep}{2pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\LARGE\bfseries Ronak Punase}\par\vspace{2pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-10pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}
\small

\maketitle
\vspace{6pt}

% ---------- SUMMARY ----------
\section{Summary}
Mobile engineer focused on Flutter with strong native Android/iOS experience. I build production apps end-to-end (architecture, UI systems, CI/CD) and have a strong track record of shipping and teaching.


% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Built a responsive design system governed by \textbf{Figma tokens} and improved UI consistency across the app.
  \item Shipped a new dynamic UI using advanced Dart patterns (mixins, factory constructors, typed enums), improving maintainability.
  \item Stabilized CI/CD workflows and reduced build failures by \textbf{40\%}.
  \item Unified Android/iOS + Firebase Distribution + Shorebird pipelines, cutting distribution time by \textbf{60--70\%}.
  \item Migrated from GitHub-hosted to local runners, reducing costs and speeding up builds by \textbf{25\%}.
\end{itemize}
\vspace{6pt}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Built Flutter apps end-to-end for tutors and students (50,000+ users), including tablet/iPad responsive UI.
  \item Integrated \textbf{Agora} native Android/iOS SDKs via a Flutter plugin, reducing implementation time by \textbf{25\%}.
  \item Shipped WhatsApp-like calling using FCM + \textbf{iOS CallKit}; also built a reusable calling plugin, cutting dev time by \textbf{75\%+}.
  \item Delivered an Instagram Stories--style feature with video caching, reducing load times by \textbf{35\%}.
  \item Built internal admin tools (CMS + customer care) on Flutter Web; led Play Store/App Store releases.
\end{itemize}


% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Flutter expense tracker shipped to Play Store and App Store.
  \item Local parsing of bank statements + SMS extraction; stored transactions in an offline-first local DB.
  \item MVVM + Bloc state management; heavy Dart usage (extensions, factory constructors).
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Built a reusable Flutter UI system + CLI and a Next.js site to distribute examples and components.
  \item Reached 12,000+ YouTube views within one week of launch.
\end{itemize}

\org{The CS Guy} \bull Passion Project \bull \href{https://youtube.com/@TheCSGuy}{youtube.com/@TheCSGuy}
\begin{itemize}
  \item Created Flutter tutorials and a free course (350,000+ total views), focused on UI engineering and best practices.
  \item Covered advanced state management (Bloc/Riverpod/Provider) and pragmatic testing/TDD.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Flutter:} Bloc, Navigator 2.0, Provider, Riverpod, Freezed, GetIt, GoRouter, MVVM, Unit Testing \\
\textbf{Mobile:} Android (Java, Kotlin, Jetpack Compose), iOS (Swift) \\
\textbf{Web:} ReactJS, NextJS (TypeScript), ExpressJS, Zustand, Redux \\
\textbf{Backend:} Firebase, MongoDB, Prisma, Supabase, ConvexDB \\
\textbf{Source Control:} Git, GitHub, GitHub Actions (CI/CD)

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}