\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center>
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} 

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Expert React developer with strong skills in JavaScript, TypeScript, Redux, Context, and data-fetching libraries. Proficient in building scalable, accessible, high-quality web interfaces and comfortable working with REST/GraphQL APIs. Detail-oriented, with experience managing complex forms and writing automated tests using Jest, React Testing Library, and Cypress. Comprehensive understanding of modern styling approaches like CSS Modules, Styled Components, and Tailwind. Experienced with build tools like Vite/Webpack, Git workflows, and CI/CD pipelines.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{React Developer} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Designed UI using React with hooks and functional components.
  \item Managed application state using Redux and data-fetching libraries.
  \item Optimized performance by handling complex forms, authentication, and REST/GraphQL APIs.
  \item Wrote automated tests for the web interfaces using Jest, React Testing Library, and Cypress.
  \item Built and maintained scalable and accessible web interfaces.
  \item Worked closely with designers and backend engineers to turn Figma designs into maintainable code.
  \item Participated in Agile sprints for estimating and delivering tasks on time.
  \item Monitored production, documented work, and reviewed code.
\end{itemize}

\role{Web Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Developed highly scalable and maintainable React applications.
  \item Worked extensively with JavaScript, TypeScript, and state management libraries.
  \item Improved application performance by implementing efficient data-fetching techniques.
  \item Collaborated with designers and backend engineers to deliver high-quality code and interfaces.
  \item Managed complex user interfaces using component-driven architecture and routing.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{React:} Hooks, Functional components, Component-driven architecture, Routing \\
\textbf{JavaScript/TypeScript:} ES6+, Async/Await, Promises, REST/GraphQL APIs \\
\textbf{Styling:} CSS Modules, Styled Components, Tailwind, Responsive design \\
\textbf{Testing Libraries:} Jest, React Testing Library, Cypress \\
\textbf{Tools:} Vite, Webpack, Git, CI/CD, Code reviews \\
\textbf{Backend:} Node.js, Express.js \\
\textbf{Others:} Performance optimization, Accessibility, Agile methodologies, Figma

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}