\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center>
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- OBJECTIVE ----------
\section{Objective}
Passionate Software Developer with deep interest in robotics and automation, skilled in C++ and Python, with experience designing and building complex systems. Looking for a challenging role where I can apply my knowledge and skills to develop high-performance and reliable robot systems and software.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Robotics Software Intern} \hfill June 2025 -- August 2025 \\
\org{XYZ Robotics} \bull \place{Remote}
\begin{itemize}
  \item Worked closely with a multidisciplinary team to build and ship robust robotics solutions.
  \item Engaged in rapid prototyping, debugging, and iteration of robotics systems.
  \item Gained deep knowledge in real-time control, kinematics, and dynamics of robots.
\end{itemize}
\vspace{12pt}
\role{Software Developer Intern} \hfill May 2024 -- August 2024 \\
\org{ABC Industries} \bull \place{Remote}
\begin{itemize}
  \item Developed perception algorithms for industrial robots, contributing to increased accuracy and performance.
  \item Gained exposure to integrating sensors, actuators, and embedded systems to optimize system performance.
  \item Learned about building testing and data pipelines, and documentation in robotics environment.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}

\org{Autonomous Mobile Robot} \bull Independent Project
\begin{itemize}
  \item Designed and built a mobile robot capable of autonomous navigation.
  \item Developed the motion planning & control algorithms in Python and C++.
  \item Worked on SLAM (Simultaneous Localization and Mapping) for this robot.
  \item Utilized ROS2 as the middleware for system integration.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Programming Languages:} C++, Python  \\
\textbf{Software:} ROS2 \\
\textbf{Robotics Skills:} Real-time control, Kinematics and Dynamics, Computer Vision, Manipulation and Planning \\
\textbf{Software Practices:} CI/CD, Testing, Documentation

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelor of Technology, Robotics} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}