\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/, 
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{% 
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Versatile iOS Developer with 5+ years of experience in building scalable applications with proficiency in Swift and Objective-C. Expertise in HTTP Live Streaming (HLS) and rich understanding of iOS app lifecycle and design patterns. Exceptional problem-solving skills and a collaborative communicator.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Senior iOS Developer} \hfill March 2023 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Developed and maintained iOS applications using \textbf{Swift} and \textbf{Objective-C}, focusing on performance optimization and user experience.
  \item Implemented \textbf{HTTP Live Streaming (HLS)} to deliver high-quality video streaming experiences.
  \item Led architectural discussions focusing on MVC and MVVM design patterns, improving team code quality.
  \item Enhanced the app’s performance by diagnosing and fixing issues, leading to a 30\% increase in user retention.
  \item Collaborated closely with UX/UI designers to build responsive interfaces following design specifications.
  \item Facilitated code reviews and mentoring sessions, promoting knowledge sharing across the team.
\end{itemize}
\vspace{12pt}
\role{iOS Developer} \hfill July 2018 -- March 2023 \\
\org{TechWave} \bull \href{https://techwave.com}{techwave.com} \hfill \place{Remote}
\begin{itemize}
  \item Designed and developed user-centric features for iOS applications using \textbf{Swift}, increasing functionality and user engagement.
  \item Participated in the complete iOS app lifecycle development, including planning, design, implementation, and deployment.
  \item Worked with a variety of architectures including MVC, MVVM, and Coordinator pattern for improved modularity.
  \item Integrated third-party libraries to enhance functionality, including real-time data streaming capabilities.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}

\org{HLS Video Streaming App} \bull Personal Project
\begin{itemize}
  \item Developed an iOS video streaming application utilizing \textbf{HTTP Live Streaming (HLS)} to deliver high-quality video content.
  \item Optimized streaming performance by implementing caching strategies and adaptive streaming techniques.
  \item Employed Swift's advanced features to ensure robust error handling and smooth playback experiences.
\end{itemize}

\org{Music Streaming App} \bull Personal Project
\begin{itemize}
  \item Created a music streaming application leveraging HLS for seamless playback across various iOS devices.
  \item Implemented offline playback capabilities using local storage solutions.
  \item Utilized MXVVM for data management and user interface binding.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{iOS Development:} Swift, Objective-C, HLS, iOS app lifecycle, MVC, MVVM, Coordinator Pattern\
\textbf{Mobile:} iOS (Swift, Objective-C)\
\textbf{Backend:} Firebase, REST APIs\
\textbf{Source Control:} Git, GitHub\
\textbf{Problem Solving:} Agile Methodologies, Code Reviews, Team Collaboration

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}