% Tailor this resume to the job expectations once you share the job description or profile URL.
% This LaTeX document is designed to be easily adjusted once the expectations are known.

\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\setlength{\parindent}{0pt}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=cyan
}

\begin{document}

\begin{center}
{\LARGE \textbf{Eshan Singh}}\\[6pt]
Gurugram, Haryana, India \quad | \quad +91-7903893191 \quad | \quad \href{mailto:accseshansingh@gmail.com}{accseshansingh@gmail.com} \\
\href{https://www.linkedin.com/in/-eshansingh/}{LinkedIn} \quad|\quad
\href{https://github.com/kevinaaaquil}{GitHub} \quad|\quad
\href{https://eshansingh.net}{Website}
\end{center}
\vspace{0.2in}

\section*{Professional Summary}
Software Development Engineer with extensive backend development and system design experience. Proficient in building scalable microservices, API design, and cloud-based infrastructure. Demonstrated leadership as Backend Lead for ABDM integration in healthcare projects, with hands-on development in Golang, TypeScript, and Node.js. Strong problem solver with experience in IAM systems, data modeling, and cross-functional collaboration.

\section*{Experience}
\begin{itemize}[leftmargin=*]
  \item \textbf{Farmako Healthcare Private Limited}, Gurugram, India \hfill Sep 2022 -- Present
  \begin{itemize}[leftmargin=1.4em]
    \item Backend Lead for ABDM (Ayushman Bharat Digital Mission) integration; designed and implemented scalable backend components enabling interoperability and compliance.
    \item Architected an internal management system with modular microservices and robust data models.
    \item Developed IAM systems for secure authentication and authorization.
  \end{itemize}
  \item \textbf{Mintair XYZ}, Gurugram, India \hfill Jan 2024 -- Present
  \begin{itemize}[leftmargin=1.4em]
    \item Software Development Engineer focused on backend services; contributed to API design, data modeling, and service reliability.
  \end{itemize}
  \item \textbf{Heiphen}, Remote \hfill Aug 2021 -- Jul 2022
  \begin{itemize}[leftmargin=1.4em]
    \item Software Development Engineer Intern; contributed to backend tasks and gained exposure to distributed systems.
  \end{itemize}
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*]
  \item \textbf{B.Tech in Computer Science and Engineering}, SRM Institute of Science and Technology, Chennai, India \hfill  Graduation: 2024
  \begin{itemize}[leftmargin=1.4em]
    \item GPA: 9.1 CGPA
  \end{itemize}
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Technical}: Golang, TypeScript, SQL, PostgreSQL, MongoDB, AWS, GCP, Azure
  \item \textbf{Soft}: Public Speaking, Debate Champion (State Level), Communication Skills
  \item \textbf{Languages}: English, Bengali, Hindi, Basic French, Basic Marathi
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*]
  \item None yet.
\end{itemize}

\section*{Job Expectations (to be provided)}
\begin{quotation}
Paste the job description text or provide the job profile URL to tailor this resume to the specific expectations. A tailored version will highlight the responsibilities, required technical skills, and impact metrics emphasized by the employer.
\end{quotation}

\end{document}