\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- OBJECTIVE ----------
\section{Objective}
Looking for a Flutter Developer position where I can apply my 3+ years of Flutter development experience to build pixel-perfect, robust, and scalable cross-platform applications. Highly skilled in writing clean and documented code, integrating APIs and Firebase services, conducting code reviews, and enthusiastic about learning and adopting modern Flutter/Dart practices.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Built pixel-perfect and responsive UIs from Figma wireframes and integrated them with RESTful APIs and Firebase.
  \item Optimized the performance and scalability of the apps by implementing advanced Dart features.
  \item Managed the full app lifecycle from design, development, testing, and deployment to Play Store/App Store.
  \item Collaborated effectively with the product, design, backend, and QA teams and conducted code reviews.
  \item Mentored junior developers and helped them to adopt modern Flutter/Dart practices.
  \item Debugged and fixed complex issues to ensure smooth operations.
\end{itemize}

\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Led and contributed to end-to-end app development for tutors, enabling collaborations between students and tutors.
  \item Shipped an Instagram Stories–inspired feature using advanced video caching and Flutter best practices.
  \item Leveraged state management solutions like BLoC, Provider, GetX, and MVVM for building reliable applications.
  \item Successfully integrated RESTful APIs, Firebase services, and third-party libraries into the apps.
  \item Contributed to design and development of resilient call billing and payout system.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Flutter:} Advanced Flutter/Dart, Bloc, Provider, GetX, MVC, MVVM, Custom Widgets, Animations, REST/JSON, Firebase (Auth, Firestore, Crashlytics, Push, Analytics) \\
\textbf{Mobile:} Native Android/iOS, Responsive UIs, Adaptive UI Design, A/B Testing and Analytics \\
\textbf{Source Control:} Git, Build/Versioning, GitHub Actions (CI/CD, Agile/Startup Processes) \\
\textbf{Soft Skills:} Excellent Problem-solving, Communication, Collaborative Team Player, Proactive, Detail-oriented UI/UX mindset

% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Led the end-to-end development and deployment of this expense tracking app on Play Store and App Store.
  \item Achieved modular and scalable architecture by utilizing MVVM with Bloc for state management.
  \item Integrated RESTful APIs, Firebase services, and third-party libraries into the app.
  \item Conducted unit, widget, and automated testing to ensure robust functionalities.
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Demonstrated advanced state management (Bloc, Riverpod, Provider) and TDD practices.
  \item Integrated RESTful APIs, Firebase services, and third-party libraries into the platform.
  \item Received 12,000+ YouTube views within a week of release.
\end{itemize}

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}