\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}


% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{%
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother


% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}


% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers


\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
A passionate iOS Engineer with a strong foundation in iOS ecosystem, equipped with profound hands-on iOS development experience. Skilled in crafting extensible platform software supporting seamless UX. Proficient in effective CI/CD pipeline development and end-to-end system design. Demonstrated excellence in mobile observability, architecture, and platform tooling.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Software Development Engineer} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Built a resilient design system following Figma tokens popularizing the principle of modularity.
  \item Pioneered robust and dynamic UI using advanced Dart features, catapulting overall project code quality.
  \item Stabilized CI/CD workflows, leading to a 40\% reduction in build failures.
  \item Implemented a cross-platform CI/CD pipeline, accelerating distribution times by 60-70\%.
  \item Optimized costs and time efficiency by replacing GitHub-hosted runners with local runners.
  \item Developed a local-first cart system, ensuring smoother UX and faster add-to-cart speed.
\end{itemize}
\vspace{12pt}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Integrated Agora's native Android and iOS SDK into a Flutter plugin, reducing development time by 25\%.
  \item Established a reliable video calling mechanism by integrating FCM, iOS CallKit, and Flutter.
  \item Developed a Flutter video calling plugin, reducing development time by over 75\%.
  \item Executed responsive designs for tablet and iPad, ensuring pixel-perfect UI across multiple screen sizes.
  \item Crafted a dedicated Flutter app for tutors facilitating collaboration between 50,000+ students and tutors.
  \item Delivered Instagram Stories-like feature using advanced video caching and optimizing load times.
  \item Led seamless deployment of PuStack and PuStack Tutor apps on Play Store and App Store.
  \item Designed a resilient call billing and payout system, increased engagement by 25\%.
\end{itemize}


% ---------- PROJECTS ----------
\section{Projects}

\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Developed an expense tracking app in Flutter for iOS and published in App Store.
  \item Used advanced Dart features for implementing the system.
  \item Introduced SMS extraction feature to collect transaction details.
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Created a Flutter UI system with reusable components and a CLI delivery system.
  \item Introduced a Next.js platform hosting Flutter WebViews for encouraging open-source contributions.
\end{itemize}

\org{The CS Guy} \bull Passion Project \bull \href{https://youtube.com/@TheCSGuy}{youtube.com/@TheCSGuy}
\begin{itemize}
  \item Produced Flutter UI centric tutorials having 200,000+ views.
  \item Launched a free Flutter tutorial series reaching 150,000+ viewers.
\end{itemize}


% ---------- SKILLS ----------
\section{Skills}

\textbf{iOS:} Swift, UIKit, Core Data, SwiftUI, Interface Builder\\
\textbf{Flutter:} Bloc, Navigator 2.0, Provider, Riverpod, Freezed, GetIt, GoRouter, MVVM, Unit Testing \\
\textbf{Web:} ReactJS, NextJS (TypeScript), ExpressJS, Zustand, Redux \\
\textbf{Backend:} Firebase, MongoDB, Prisma, Supabase, ConvexDB \\
\textbf{CI/CD:} Git, GitHub, GitHub Actions (CI/CD), Jenkins, Xcode Server\\
\textbf{Others:} Performance Optimization, Debugging, Agile Methodologies\\

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}