
\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/,  
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{}% 
\def\@sect#1#2#3#4#5#6[#7]#8{% 
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{% 
      \MakeUppercase{#8}\\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Motivated Flutter Developer eager to leverage skills in Dart and mobile development. Proficient in Flutter framework, managing Firebase services, creating UI from Figma designs, and writing clean code using best practices.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{SDE} \hfill March 2025 -- Present \\
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Implemented a responsive design system governed by \textbf{Figma tokens}.  
  \item Managed Firebase services for real-time data storage and user authentication, enhancing user experience.  
  \item Developed robust features using advanced Dart functionalities, improving overall code quality.  
  \item Resolved issues efficiently through strong problem-solving skills, leading to a 40\% reduction in build failures.  
  \item Created user-friendly UI components aligned with Figma designs, ensuring consistency.  
\end{itemize}
\vspace{12pt}
\role{Flutter Developer} \hfill July 2021 -- March 2025 \\
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Integrated \textbf{Agora’s} SDK into a Flutter plugin, streamlining video call functionalities.  
  \item Developed a dedicated Flutter app for tutors and students, enhancing collaboration for 50,000+ users.  
  \item Implemented state management using Bloc and Riverpod, ensuring responsive UI.  
  \item Led the deployment of apps on Play Store and App Store, maintaining high standards of quality.  
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}
\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Expense tracking app, utilizing advanced Dart features and built with Flutter.  
  \item Integrated local database for storing transaction details, enhancing app performance.  
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Built a UI system with reusable components, encouraging collaboration in the Flutter community.  
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Mobile Development:} Flutter, Dart, Firebase, API Integration  \\
\textbf{State Management:} Bloc, Riverpod \\ 
\textbf{Web Development:} ReactJS, NextJS, ExpressJS  \\
\textbf{Database:} Firebase, MongoDB  \\
\textbf{Tools:} Git, GitHub, CI/CD  \\
\textbf{Problem Solving:} Organized and methodical approach to debugging and improving code quality

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}