\documentclass[10pt, letterpaper]{article}

% ---------- Fonts & layout ----------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

% Set SourceSans3 as the main font
\setmainfont{SourceSans3}[
  Path = ./sourceSans/, 
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic
]

% ---------- Colors ----------
\definecolor{Primary}{RGB}{23,43,77}
\definecolor{RuleGray}{gray}{0.25}
\definecolor{lightblue}{RGB}{10, 132, 255}

% ---------- PDF meta ----------
\hypersetup {
  pdftitle={Resume - Ronak Punase},
  pdfauthor={Ronak Punase},
  colorlinks=true,
  linkcolor=lightblue,
  urlcolor=lightblue,
  citecolor=lightblue
}

% ---------- Section styling ----------
\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}{10pt}{6pt}{%
    \Large\bfseries\color{black}%
  }%
}
\renewcommand{\@seccntformat}[1]{} 
\def\@sect#1#2#3#4#5#6[#7]#8{%
  \ifnum #2>\c@secnumdepth
    \let\@svsec\@empty
  \else
    \refstepcounter{#1}%
    \let\@svsec\@empty
  \fi
  \begingroup
    #6{% 
      \MakeUppercase{#8}\[-4pt]%
      \textcolor{RuleGray}{\rule{\linewidth}{0.5pt}}%
    }%
  \endgroup
  \@xsect{#5}%
}
\makeatother

% ---------- Lists ----------
\setlength{\leftmargini}{0pt}
\setlength{\itemindent}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\parsep}{0pt}

% ---------- Small helpers ----------
\newcommand{\bull}{\kern0.45em\textbullet\kern0.45em}
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\org}[1]{\textbf{#1}}
\newcommand{\place}[1]{\textit{#1}}
\newcommand{\blackLink}[2]{\href{#1}{\textcolor{black}{#2}}}
\newcommand{\blueLink}[2]{\href{#1}{\textcolor{lightblue}{#2}}}

% ---------- Header ----------
\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries Ronak Punase}\par\vspace{6pt}
    {\color{Primary}
      Bhopal, India \bull
      \blackLink{mailto:punase.ronak99@gmail.com}{punase.ronak99@gmail.com} \bull
      +91 86025 59742 \bull
      \blackLink{https://linkedin.com/in/ronak-punase}{in/ronak-punase} \bull
      \blackLink{http://ronakpunase.dev}{ronakpunase.dev}
    }
  \end{center}
  \vspace{-8pt}
}
\makeatother

% ---------- Page Style ----------
\pagestyle{empty} % Add this line to remove page numbers

\begin{document}

\maketitle
\vspace{15pt}

% ---------- SUMMARY ----------
\section{Summary}
Analytical and detail-oriented Program Manager with expertise in driving cross-functional projects that enhance user safety and address business issues through data analysis. Proficient in SQL and program management with a collaborative approach to stakeholders and ability to influence executive audiences. Looking to leverage my skills in analytics at YouTube.

% ---------- EXPERIENCE ----------
\section{Experience}
\role{Program Manager} \hfill March 2025 -- Present \
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Led cross-functional analytics initiatives focused on user safety, enhancing processes by implementing key performance metrics.
  \item Managed teams to improve data-driven decision-making processes, delivering insights via SQL analysis that addressed critical business challenges.
  \item Communicated project progress and metrics to stakeholders, fostering transparency and engagement.
  \item Established systemic frameworks for effective program management, improving the productivity of analytics projects by 35\%.
\end{itemize}
\vspace{12pt}
\role{SDE} \hfill June 2023 -- March 2025 \
\org{Farmako} \bull \href{https://farmako.ai}{farmako.ai} \hfill \place{Gurugram, Haryana}
\begin{itemize}
  \item Implemented a responsive design system governed by \textbf{Figma tokens}, which enhanced user interface consistency across applications.
  \item Developed and stabilized CI/CD workflows, reducing build failures by 40\% and improving project turnaround time.
  \item Collaborated with cross-functional teams to define and address user safety measures through meticulous data analysis.
\end{itemize}
\vspace{12pt}
\role{Flutter Developer} \hfill July 2021 -- June 2023 \
\org{PuStack} \bull \href{https://pustack.com}{pustack.com} \hfill \place{Remote}
\begin{itemize}
  \item Integrated user feedback mechanisms into applications, enabling real-time insights and improving user safety protocols.
  \item Established a reliable video calling mechanism reducing downtime, emphasizing user experience (UX) and safety.
  \item Analyzed user engagement data to continually refine features, resulting in a 25\% increase in interactions on the platform.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}
\org{MyMoney} \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Designed an expense tracking app utilizing SQL for transaction analysis, published to app stores.
  \item Implemented features that extracted bank transactions locally, enhancing user data management and privacy.
\end{itemize}

\org{Majestic UI} \bull Passion Project \bull \href{https://majesticui.com}{majesticui.com}
\begin{itemize}
  \item Developed a UI system for Flutter aimed at fostering safe development practices and enhancing contributions to user safety in software projects.
\end{itemize}

\org{The CS Guy} \bull Passion Project \bull \href{https://youtube.com/@TheCSGuy}{youtube.com/@TheCSGuy}
\begin{itemize}
  \item Produced advanced tutorials on Flutter emphasizing state management practices, garnering significant engagement and outreach.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}
\textbf{Analytics:} Data Analysis, SQL, Metrics Development \ \ 
\textbf{Project Management:} Cross-Functional Project Coordination, Stakeholder Communication, Process Improvement \ \ 
\textbf{Flutter:} Bloc, Navigator 2.0, Provider, Riverpod, Freezed, GetIt, GoRouter \ \ 
\textbf{Mobile:} Android (Java, Kotlin), iOS (Swift) \ \ 
\textbf{Web:} ReactJS, NextJS (TypeScript) \ \ 
\textbf{Backend:} Firebase, MongoDB, Prisma \ \ 
\textbf{Source Control:} Git, GitHub, GitHub Actions (CI/CD)

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bachelors of Engineering} \bull RGPV University \bull Bhopal, MP \bull 2021 \bull GPA: 4.25/5.0

\end{document}
